---
title: "clean_data"
author: "Zain"
date: "2025-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(ggplot2)
library(scales)
library(corrr)
library(corrplot)
install.packages("ggmosaic", dependencies = TRUE)
library(ggmosaic)
library(ggh4x)
library(patchwork)
library(stringr)
```

```{r}
## read in data
data <- read_csv(here("data", "immigration.csv"))

# jsut first 100 observatios

small_data <- data %>%
  slice(1:100)

#save small data as csv

write_csv(small_data, "data/small_data.csv")

```


```{r}
## run correlation on immigration numbers, asylum and concerns about the channel ## 





## wrangle data for immigration and asylum preferences by segment ##

# Updated collapse_categories function to handle NA and "Don't know" better
collapse_categories <- function(response) {
  case_when(
    is.na(response) ~ "Don't know",
    str_detect(response, "significantly increase|slightly increase") ~ "Increase numbers",
    str_detect(response, "keep the number the same") ~ "Stay the same", 
    str_detect(response, "significantly reduce|slightly reduce") ~ "Reduce numbers",
    str_detect(response, "Don't know|don't know|Dont know|dont know") ~ "Don't know",
    TRUE ~ "Don't know"  # Catch any remaining cases as "Don't know"
  )
}


```

```{r}
# Update  egment attitudes creation to include weights
segment_attitudes_weighted <- data %>%
  filter(!is.na(segment), !is.na(immigrant_numbers), !is.na(refugees_numbers), !is.na(UKNatRepWeight)) %>%
  mutate(
    immigrant_attitude = collapse_categories(immigrant_numbers),
    refugee_attitude = collapse_categories(refugees_numbers)
  ) %>%
  select(segment, immigrant_attitude, refugee_attitude, UKNatRepWeight)

# Create weighted plot data
plot_segment_attitude_weighted <- segment_attitudes_weighted %>%
  pivot_longer(
    cols = c(immigrant_attitude, refugee_attitude),
    names_to = "question_type", 
    values_to = "attitude"
  ) %>%
  mutate(
    question_type = case_when(
      question_type == "immigrant_attitude" ~ "Immigrants",
      question_type == "refugee_attitude" ~ "Refugees"
    )
  ) %>%
  filter(!is.na(attitude)) %>%
  # Group and calculate weighted percentages
  group_by(segment, question_type, attitude) %>%
  summarise(weighted_n = sum(UKNatRepWeight, na.rm = TRUE), .groups = "drop") %>%
  group_by(segment, question_type) %>%
  mutate(
    total_weighted = sum(weighted_n),
    percentage = (weighted_n / total_weighted) * 100
  ) %>%
  ungroup() %>%
  mutate(
    attitude = factor(attitude, levels = c("Reduce numbers", "Stay the same", "Increase numbers", "Don't know")),
    # Add custom segment ordering
    segment = factor(segment, levels = c(
      "Progressive Activists", 
      "Civic Pragmatists", 
      "Disengaged Battlers", 
      "Established Liberals", 
      "Loyal Nationals", 
      "Disengaged Traditionalists",
      "Backbone Conservatives"
    ))
  )

# Updated "Reduce numbers" plot with weights, no gridlines, and custom ordering
segment_reduce <- plot_segment_attitude_weighted %>%
  filter(attitude == "Reduce numbers") %>%
  ggplot(aes(x = question_type, y = percentage, fill = question_type)) +
  geom_col(alpha = 0.8, width = 0.6) +
  geom_text(aes(label = paste0(round(percentage, 0), "%")), 
            vjust = -0.5, size = 3) +
  facet_wrap(~ segment, ncol = 3) +
  scale_fill_manual(values = c("Immigrants" = "#d73027", "Refugees" = "#2166ac")) +
  labs(
    title = "Percentage Wanting to Reduce Numbers",
    subtitle = "",
    x = "",
    y = "Percentage wanting to reduce numbers"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    # Remove gridlines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  ylim(0, 100)

print(segment_reduce)


ggsave("plots_presentation/segment_reduce.svg", plot = segment_reduce, width = 7, height = 5, units = "in")


```





```{r}

# Option 1: Faceted by segment - Stacked bars
p1 <- plot_segment_attitude %>%
  ggplot(aes(x = question_type, y = percentage, fill = attitude)) +
  geom_col(position = "stack") +
  facet_wrap(~ segment, ncol = 3) +
  scale_fill_manual(
    values = c("Reduce numbers" = "#d73027", 
               "Stay the same" = "#fee08b", 
               "Increase numbers" = "#4575b4", 
               "Don't know" = "#999999")
  ) +
  labs(
    title = "Immigration vs Refugee Attitudes by Segment",
    subtitle = "Percentage distribution within each segment",
    x = "",
    y = "Percentage",
    fill = "Attitude"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p1)

```

```{r}

# Option 2: Side-by-side comparison
p2 <- plot_segment_attitude %>%
  ggplot(aes(x = attitude, y = percentage, fill = question_type)) +
  geom_col(position = "dodge", alpha = 0.8) +
  facet_wrap(~ segment, ncol = 3) +
  scale_fill_manual(values = c("Immigrants" = "#2166ac", "Refugees" = "#762a83")) +
  labs(
    title = "Immigration vs Refugee Attitudes by Segment",
    subtitle = "Direct comparison of attitudes within each segment",
    x = "Attitude",
    y = "Percentage",
    fill = "Question Type"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p2)


```

```{r}


p3_weighted <- plot_segment_attitude_weighted %>%
  filter(attitude == "Reduce numbers") %>%
  ggplot(aes(x = question_type, y = percentage, fill = question_type)) +
  geom_col(alpha = 0.8, width = 0.6) +
  geom_text(aes(label = paste0(round(percentage, 0), "%")), 
            vjust = -0.5, size = 3) +
  facet_wrap(~ segment, ncol = 3) +
  scale_fill_manual(values = c("Immigrants" = "#d73027", "Refugees" = "#2166ac")) +
  labs(
    title = 'Percentage Wanting to "Reduce Numbers" by Segment (Weighted)',
    subtitle = "Nationally representative results using UKNatRepWeight",
    x = "",
    y = "Percentage wanting to reduce numbers"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  ylim(0, 100)

print(p3_weighted)

```

```{r}

p4_weighted <- plot_segment_attitude_weighted %>%
  filter(attitude == "Reduce numbers") %>%
  mutate(segment = factor(segment, levels = c("Progressive Activists", 
                                              "Civic Pragmatists", 
                                              "Disengaged Battlers", 
                                              "Established Liberals", 
                                              "Loyal Nationals",
                                              "Disengaged Traditionalists",
                                              "Backbone Conservatives"))) %>%
  ggplot(aes(x = question_type, y = percentage, fill = question_type)) +
  geom_col(alpha = 0.8, width = 0.6) +
  geom_text(aes(label = paste0(round(percentage, 0), "%")), 
            vjust = -0.5, size = 3) +
  facet_wrap(~ segment, ncol = 3) +
  scale_fill_manual(values = c("Immigrants" = "#d73027", "Refugees" = "#2166ac")) +
  labs(
    title = 'Percentage Wanting to "Reduce Numbers" by Segment',
    subtitle = "Comparing attitudes toward immigrants vs refugees",
    x = "",
    y = "Percentage wanting to reduce numbers"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  ylim(0, 100)

print(p4_weighted)  # Note: changed from p4 to p4_weighted

```

```{r}


## most important issue ## 



biggestissue_cols <- names(data)[str_starts(names(data), "biggestissue:")]
print("BiggestIssue columns found:")
print(biggestissue_cols)

# Create a function to clean issue names (remove "biggestissue:" prefix)
clean_issue_name <- function(col_name) {
  str_remove(col_name, "biggestissue:")
}

# Method 1: Calculate weighted proportions for each issue
issue_summary <- data %>%
  filter(!is.na(UKNatRepWeight)) %>%
  select(all_of(biggestissue_cols), UKNatRepWeight) %>%
  pivot_longer(
    cols = all_of(biggestissue_cols),
    names_to = "issue",
    values_to = "selection"
  ) %>%
  mutate(
    issue = clean_issue_name(issue),
    selected = ifelse(selection == "Selected", 1, 0)
  ) %>%
  filter(!is.na(selected)) %>%
  group_by(issue) %>%
  summarise(
    # Weighted calculations
    weighted_selected = sum(selected * UKNatRepWeight, na.rm = TRUE),
    total_weighted = sum(UKNatRepWeight, na.rm = TRUE),
    weighted_percentage = round((weighted_selected / total_weighted) * 100, 1),
    
    # Unweighted for comparison
    unweighted_selected = sum(selected, na.rm = TRUE),
    total_unweighted = n(),
    unweighted_percentage = round((unweighted_selected / total_unweighted) * 100, 1),
    
    .groups = "drop"
  ) %>%
  arrange(desc(weighted_percentage))

print("Issue Selection Summary (Weighted vs Unweighted):")
print(issue_summary)

```


```{r}

# Create the plot for the most important issues

top_issues_plot <- issue_summary %>%
  slice_head(n = 12) %>%  # Show top 12 issues
  ggplot(aes(x = reorder(issue, weighted_percentage), y = weighted_percentage)) +
  geom_col(fill = "#2166ac", alpha = 0.8) +
  geom_text(aes(label = paste0(round(weighted_percentage, 0), "%")),, 
            hjust = -0.1, size = 3) +
  coord_flip() +
  labs(
    title = "Most Important Issues",
    subtitle = "Percentage of respondents selecting each issue as one of the most important",
    x = "Issue",
    y = "Percentage of respondents",
    caption = "Respondents could select up to 3 issues."
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.text.y = element_text(size = 9),
    # Remove gridlines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
 
  ylim(0, max(issue_summary$weighted_percentage) * 1.1)

print(top_issues_plot)


```


```{r}

## create demographics for age, gender, financnial security,  education and most important issue



# Step 1: Select relevant variables and create binary variables
plot_data <- data %>%
  select(
    gender, age_grouped, degree, finances, votingintention_headline,
    `biggestissue:Asylum seekers crossing the channel`,
    `biggestissue:Levels of immigration`,
    UKNatRepWeight
  ) %>%
  filter(!is.na(UKNatRepWeight)) %>%
  # Create binary variables
  mutate(
    # Age binary: <55 vs 55+
    age_binary = case_when(
      str_detect(age_grouped, "18-24|25-34|35-44|45-54") ~ "Under 55",
      str_detect(age_grouped, "55-64|65-74|75\\+") ~ "55+",
      TRUE ~ NA_character_
    ),
    
    # Voting intention: Reform/Conservative vs Other
    vote_binary = case_when(
      votingintention_headline %in% c("Reform UK", "Conservative") ~ "Reform/Conservative",
      !is.na(votingintention_headline) ~ "Other parties",
      TRUE ~ NA_character_
    ),
    
    # Financial security binary
    financial_security = case_when(
      finances %in% c(
        "I am very comfortable financially", 
        "I am relatively comfortable financially"
      ) ~ "Financially comfortable",
      finances %in% c(
        "I can only just afford my costs and often struggle to make ends meet",
        "I cannot afford my costs and often have to go without essentials like food and heating",
        "I do not have money for luxuries but can normally comfortably cover the essentials"
      ) ~ "Financially constrained",
      TRUE ~ NA_character_
    ),
    
    # Create immigration/asylum issue indicator
    selected_immigration_asylum = case_when(
      `biggestissue:Asylum seekers crossing the channel` == "Selected" | 
      `biggestissue:Levels of immigration` == "Selected" ~ 1,
      TRUE ~ 0
    )
  ) %>%
  # Filter out NAs in key variables
  filter(
    !is.na(gender),
    !is.na(age_binary), 
    !is.na(financial_security),
    !is.na(vote_binary)
  )

# Check the created binary variables
cat("Age binary distribution:\n")
print(table(plot_data$age_binary, useNA = "ifany"))

cat("\nVote binary distribution:\n") 
print(table(plot_data$vote_binary, useNA = "ifany"))

cat("\nFinancial security distribution:\n")
print(table(plot_data$financial_security, useNA = "ifany"))

cat("\nImmigration/Asylum selection distribution:\n")
print(table(plot_data$selected_immigration_asylum))

```


```{r}

# Function to calculate weighted percentages for each demographic group
calculate_weighted_props <- function(data, group_vars) {
  data %>%
    group_by(across(all_of(group_vars))) %>%
    summarise(
      weighted_selected = sum(selected_immigration_asylum * UKNatRepWeight, na.rm = TRUE),
      total_weighted = sum(UKNatRepWeight, na.rm = TRUE),
      weighted_percentage = round((weighted_selected / total_weighted) * 100, 0),
      .groups = "drop"
    )
}

# Calculate proportions by gender
gender_props <- calculate_weighted_props(plot_data, "gender")

# Calculate proportions by age
age_props <- calculate_weighted_props(plot_data, "age_binary")

# Calculate proportions by financial security
finance_props <- calculate_weighted_props(plot_data, "financial_security")

# Calculate proportions by voting intention
vote_props <- calculate_weighted_props(plot_data, "vote_binary")

# Combine all for faceted plot
combined_props <- bind_rows(
  gender_props %>% mutate(demographic = "Gender", group = gender),
  age_props %>% mutate(demographic = "Age", group = age_binary),
  finance_props %>% mutate(demographic = "Financial Security", group = financial_security),
  vote_props %>% mutate(demographic = "Voting Intention", group = vote_binary)
) %>%
  select(demographic, group, weighted_percentage)

# Create faceted plot
faceted_plot <- combined_props %>%
  ggplot(aes(x = group, y = weighted_percentage, fill = group)) +
  geom_col(alpha = 0.8, width = 0.7) +
  geom_text(aes(label = paste0(weighted_percentage, "%")), 
            vjust = -0.5, size = 3.5, fontface = "bold") +
  facet_wrap(~ demographic, scales = "free_x", ncol = 2) +
  scale_fill_brewer(type = "qual", palette = "Set2") +
  labs(
    title = "Immigration/Asylum as Most Important Issue by Demographics",
    subtitle = "Percentage selecting 'Levels of immigration' or 'Asylum seekers crossing the channel'",
    x = "",
    y = "Percentage selecting immigration/asylum issues",
    caption = "Weighted results using UKNatRepWeight"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    plot.title = element_text(size = 14, face = "bold"),
    legend.position = "none"
  ) +
  ylim(0, max(combined_props$weighted_percentage) * 1.15)

print(faceted_plot)

```

```{r}



plot_data <- data %>%
  select(
    gender, age_grouped, degree, finances, votingintention_headline,
    `biggestissue:Asylum seekers crossing the channel`,
    `biggestissue:Levels of immigration`,
    UKNatRepWeight
  ) %>%
  filter(!is.na(UKNatRepWeight)) %>%
  # Create binary variables
  mutate(
    # Age binary: <55 vs 55+
    age_binary = case_when(
      str_detect(age_grouped, "18-24|25-34|35-44|45-54") ~ "Under 55",
      str_detect(age_grouped, "55-64|65-74|75\\+") ~ "55+",
      TRUE ~ NA_character_
    ),
    
    # Voting intention: Reform/Conservative vs Other
    vote_binary = case_when(
      votingintention_headline %in% c("Reform UK", "Conservative") ~ "Reform/Conservative",
      !is.na(votingintention_headline) ~ "Other parties",
      TRUE ~ NA_character_
    ),
    
    # Financial security binary
    financial_security = case_when(
      finances %in% c(
        "I am very comfortable financially", 
        "I am relatively comfortable financially"
      ) ~ "Financially comfortable",
      finances %in% c(
        "I do not have money for luxuries but can normally comfortably cover the essentials",
        "I can only just afford my costs and often struggle to make ends meet",
        "I cannot afford my costs and often have to go without essentials like food and heating"
      ) ~ "Financially constrained",
      TRUE ~ NA_character_
    ),
    
 
# Degree binary
degree_binary = case_when(
  degree == "Degree" ~ "Has degree",
  degree == "No degree" ~ "No degree",
  TRUE ~ NA_character_
  
),
    
    # Create immigration/asylum issue indicator
    selected_immigration_asylum = case_when(
      `biggestissue:Asylum seekers crossing the channel` == "Selected" | 
      `biggestissue:Levels of immigration` == "Selected" ~ 1,
      TRUE ~ 0
    )
  ) %>%
  # Filter out NAs in key variables
  filter(
    !is.na(gender),
    !is.na(age_binary), 
    !is.na(financial_security),
    !is.na(vote_binary),
    !is.na(degree_binary)
  )

# Function to calculate what percentage WITHIN each group selected the issue
calculate_within_group_props <- function(data, group_var) {
  data %>%
    group_by(.data[[group_var]]) %>%
    summarise(
      total_weighted = sum(UKNatRepWeight, na.rm = TRUE),
      selected_weighted = sum(selected_immigration_asylum * UKNatRepWeight, na.rm = TRUE),
      percentage_within_group = round((selected_weighted / total_weighted) * 100, 0),
      .groups = "drop"
    ) %>%
    rename(group = 1) %>%
    mutate(demographic = group_var)
}

# Calculate proportions WITHIN each demographic group
gender_within_group <- calculate_within_group_props(plot_data, "gender")
age_within_group <- calculate_within_group_props(plot_data, "age_binary") 
finance_within_group <- calculate_within_group_props(plot_data, "financial_security")
vote_within_group <- calculate_within_group_props(plot_data, "vote_binary")
degree_within_group <- calculate_within_group_props(plot_data, "degree_binary")

# Combine all for faceted plot
within_group_props <- bind_rows(
  gender_within_group,
  age_within_group,
  finance_within_group, 
  vote_within_group,
  degree_within_group
) %>%
  mutate(
    demographic = case_when(
      demographic == "gender" ~ "Gender",
      demographic == "age_binary" ~ "Age",
      demographic == "financial_security" ~ "Financial Security", 
      demographic == "vote_binary" ~ "Voting Intention",
      demographic == "degree_binary" ~ "Education",
      TRUE ~ demographic
    )
  )

print("Percentage within each group selecting immigration/asylum as most important:")
print(within_group_props)

```

```{r}
# Create faceted plot showing percentage WITHIN each group
within_group_faceted_plot <- within_group_props %>%
  ggplot(aes(x = group, y = percentage_within_group, fill = group)) +
  geom_col(alpha = 0.8, width = 0.7) +
  geom_text(aes(label = paste0(percentage_within_group, "%")), 
            vjust = -0.5, size = 3.5, fontface = "bold") +
  facet_wrap(~ demographic, scales = "free_x", ncol = 3) +
  scale_fill_brewer(type = "qual", palette = "Set2") +
  labs(
    title = "Immigration/Asylum as Most Important Issue: Within-Group Percentages",
    subtitle = "What percentage of each demographic group selected immigration/asylum issues",
    x = "",
    y = "Percentage within group selecting immigration/asylum",
    caption = ""
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    plot.title = element_text(size = 14, face = "bold"),
    legend.position = "none",
    panel.grid.minor = element_blank(),
     panel.grid.major = element_blank()  # Add this line
  ) +
  ylim(0, max(within_group_props$percentage_within_group) * 1.15)

print(within_group_faceted_plot)

```

```{r}

# Alternative: Side-by-side comparison plot
within_group_comparison_plot <- within_group_props %>%
  ggplot(aes(x = reorder(group, percentage_within_group), 
             y = percentage_within_group, 
             fill = demographic)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(percentage_within_group, "%")), 
            hjust = -0.1, size = 3) +
  facet_wrap(~ demographic, scales = "free", ncol = 2) +
  coord_flip() +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  labs(
    title = "Priority Attached to Immigration/Asylum By Voter Chracteristics",
    subtitle = "Percentage within each group selecting these as most important issues",
    x = "",
    y = "Percentage within group",
    caption = ""
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.x = element_blank(),
    plot.title = element_text(size = 14, face = "bold"),
    legend.position = "none",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()  # Add this line
  ) +  
  ylim(0, max(within_group_props$percentage_within_group) * 1.15)

print(within_group_comparison_plot)

```

```{r}

# Filter to only those who selected immigration/asylum as most important issue
immigration_respondents <- plot_data %>%
  filter(selected_immigration_asylum == 1)

# Function to calculate demographic composition among immigration issue selectors
calculate_composition_props <- function(data, group_var) {
  data %>%
    group_by(.data[[group_var]]) %>%
    summarise(
      weighted_count = sum(UKNatRepWeight, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      total_weighted = sum(weighted_count),
      percentage_of_immigration_selectors = round((weighted_count / total_weighted) * 100, 0)
    ) %>%
    rename(group = 1) %>%
    mutate(demographic = group_var)
}

# Calculate demographic composition among those who selected immigration/asylum
gender_composition <- calculate_composition_props(immigration_respondents, "gender")
age_composition <- calculate_composition_props(immigration_respondents, "age_binary") 
finance_composition <- calculate_composition_props(immigration_respondents, "financial_security")
vote_composition <- calculate_composition_props(immigration_respondents, "vote_binary")
degree_composition <- calculate_composition_props(immigration_respondents, "degree_binary")


# Combine all demographic compositions
immigration_composition <- bind_rows(
  gender_composition,
  age_composition,
  finance_composition, 
  vote_composition,
  degree_composition
) %>%
  mutate(
    demographic = case_when(
      demographic == "gender" ~ "Gender",
      demographic == "age_binary" ~ "Age",
      demographic == "financial_security" ~ "Financial Security", 
      demographic == "vote_binary" ~ "Voting Intention",
      demographic == "degree_binary" ~ "Education",
      TRUE ~ demographic
    )
  )

# Reorder groups so pairs will be vertically aligned in a 2-row legend
desired_order <- c(
  "Male", "55+", "Financially comfortable", "Reform/Conservative", "Has degree",
  "Female", "Under 55", "Financially constrained", "Other parties", "No degree"
)

# Update the immigration_composition with the new order
immigration_composition$group <- factor(immigration_composition$group, levels = desired_order)
  

# Create a custom color palette with dark yellow and dark green
custom_colors <- c("#B8860B", "#006400")  # DarkGoldenrod and DarkGreen

 # Create individual stacked horizontal bar charts for each demographic
# Create individual stacked horizontal bar charts for each demographic
composition_horizontal_plots <- immigration_composition %>%
  split(.$demographic) %>%
  map(function(df) {
    demographic_name <- unique(df$demographic)
    
    # Create a color mapping based on number of groups
    n_groups <- nrow(df)
    colors_to_use <- custom_colors[1:n_groups]
    names(colors_to_use) <- df$group
    
    # Reorder the factor levels to match our desired legend order
    df$group <- factor(df$group, levels = immigration_composition$group)
    
    ggplot(df, aes(x = 1, y = percentage_of_immigration_selectors, fill = group)) +
      geom_col(width = 0.6, alpha = 0.8) +
      geom_text(aes(label = paste0(percentage_of_immigration_selectors, "%")), 
                position = position_stack(vjust = 0.5), 
                color = "white", fontface = "bold", size = 3.5) +
      coord_flip() +
      scale_fill_manual(values = colors_to_use) +
      labs(
        title = paste("Composition by", demographic_name),
        subtitle = "Among those who selected immigration/asylum as most important issue",
        x = "",
        y = "Percentage of immigration/asylum selectors",
        fill = "Group"
      ) +
      theme_minimal() +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = 12, face = "bold"),
        legend.position = "bottom",
        legend.box = "horizontal",
        legend.direction = "horizontal",
        legend.box.just = "center"
      ) +
      guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
      ylim(0, 100)
  })
# Print each composition plot
iwalk(composition_horizontal_plots, ~ {
  cat("\n", names(composition_horizontal_plots)[.y], "\n")
  print(.x)
})

# For the combined plot
all_groups <- unique(immigration_composition$group)
extended_colors <- rep(custom_colors, length.out = length(all_groups))
names(extended_colors) <- all_groups

# Combined faceted stacked horizontal bars
combined_composition_horizontal <- immigration_composition %>%
  ggplot(aes(x = demographic, y = percentage_of_immigration_selectors, fill = group)) +
  geom_col(alpha = 0.8, width = 0.7) +
  geom_text(aes(label = paste0(percentage_of_immigration_selectors, "%")), 
            position = position_stack(vjust = 0.5), 
            color = "white", fontface = "bold", size = 3) +
  coord_flip() +
  scale_fill_manual(values = extended_colors) +
  labs(
    title = "Who See Immigration or Asylum as The Most Important Issue ",
    subtitle = "",
    x = "Demographic Categories",
    y = "Percentage of immigration/asylum selectors",
    fill = "Group",
    caption = "Weighted results using UKNatRepWeight"
  ) +
  theme_minimal() +
theme(
  plot.title = element_text(size = 14, face = "bold"),
  legend.position = "bottom",
  legend.box = "horizontal", 
  legend.direction = "horizontal",
  legend.box.just = "center",
  panel.grid.minor = element_blank()
) +
guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
ylim(0, 100)
print(combined_composition_horizontal)

# Create a summary table showing the exact percentages
composition_summary_table <- immigration_composition %>%
  select(demographic, group, percentage_of_immigration_selectors) %>%
  pivot_wider(names_from = group, values_from = percentage_of_immigration_selectors, values_fill = 0) %>%
  arrange(demographic)

print("Demographic Composition of Immigration/Asylum Issue Selectors:")
print(composition_summary_table)

```


```{r}
## corelation heatmap of demogrpahic variables and immigration and asylum attius  ##


df <- data %>%  
  mutate(
    immigrant_num = case_when(
      immigrant_numbers == "Government should significantly reduce the numbers"  ~ 1,
      immigrant_numbers == "Government should slightly reduce the numbers"  ~ 2,
      immigrant_numbers == "Government should keep the number the same"  ~ 3,
       immigrant_numbers == "Government should slightly increase the numbers" ~ 4,
       immigrant_numbers == "Government should significantly increase the numbers"  ~ 5,
      TRUE ~ NA_real_
    ),
    
    # Order so higher = more typically pro-immigration demographics
    gender_num = case_when(
      gender == "Male" ~ 1,      # Research often shows men slightly less pro-immigration
      gender == "Female" ~ 2,    # Women often more pro-immigration
      TRUE ~ NA_real_
    ),
    
    education_num = case_when(
      degree == "No high school" ~ 1,
      degree == "High school" ~ 2,
      degree == "Some college" ~ 3,
      degree == "Bachelor's" ~ 4,
      degree == "Graduate degree" ~ 5,  # Higher education typically more pro-immigration
      TRUE ~ NA_real_
    ),
    
    urbanrural_num = case_when(
  urbanrural == "Rural Area" ~ 1,
  urbanrural == "Village" ~ 2,
  urbanrural == "Small Town" ~ 3,
  urbanrural == "Large Town" ~ 4,
  urbanrural == "Suburbs" ~ 5,
  urbanrural == "Urban/City Centre" ~ 6,
  TRUE ~ NA_real_
),

degree_num = case_when(
      degree == "No degree" ~ 1,
      degree == "Degree" ~ 2,
      TRUE ~ NA_real_
    ),

financial_num = case_when(
  finances == "I am very comfortable financially" ~ 5,
  finances == "I am relatively comfortable financially" ~ 4, 
  finances == "I do not have money for luxuries but can normally comfortably cover the essentials" ~ 3,
  finances == "I can only just afford my costs and often struggle to make ends meet" ~ 2,
  finances == "I cannot afford my costs and often have to go without essentials like food and heating" ~ 1,
),
    
    # For political variables, order by typical pro-immigration stance
    voting_num = case_when(
      votingintention_headline == "Reform UK" ~ 1,
      votingintention_headline == "Conservative" ~ 2,
      votingintention_headline == "Liberal Democrat" ~ 3,
      votingintention_headline == "Labour" ~ 4,
      votingintention_headline == "The Green Party" ~5,
      TRUE ~ NA_real_
    )
  )

# 2. DATA WRANGLING FOR FACETING 
facet_data <- df %>%
  select(immigrant_num, gender_num, degree_num, urbanrural_num, 
         financial_num, voting_num) %>%
  # Remove rows with missing immigration attitude
  filter(!is.na(immigrant_num)) %>%
  pivot_longer(
    cols = -immigrant_num,
    names_to = "demographic",
    values_to = "value"
  ) %>%
  # Remove rows with missing demographic values
  filter(!is.na(value)) %>%
  group_by(demographic) %>%
  summarise(
    correlation = cor(immigrant_num, value, 
                     method = "spearman", use = "complete.obs"),
    n = n(), # Add sample size
    .groups = "drop"
  ) %>%
  # Clean up demographic labels for display
  mutate(
    demographic_clean = case_when(
      demographic == "gender_num" ~ "Gender",
      demographic == "degree_num" ~ "Education",
      demographic == "urbanrural_num" ~ "Urban/Rural",
      demographic == "financial_num" ~ "Financial Sitution",
      demographic == "voting_num" ~ "Voting Intention",
      TRUE ~ demographic
    )
  )

# 3. CREATE FACETED HEATMAP 
ggplot(facet_data, aes(x = "", y = "", fill = correlation)) +
  geom_tile(color = "white", width = 0.9, height = 0.9) +
  geom_text(aes(label = paste0(round(correlation, 2), "\n(n=", n, ")")), 
            color = "black", size = 3.5, fontface = "bold") +
  facet_wrap(~demographic_clean, nrow = 1) +
  scale_fill_gradient2(
    low = "#E41A1C",   # Red for negative
    mid = "white",      # White for neutral
    high = "#377EB8",   # Blue for positive
    midpoint = 0,
    limits = c(-1, 1),
    name = "Correlation\n(Spearman's ρ)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    strip.text = element_text(face = "bold", size = 10),
    legend.position = "right",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    plot.margin = margin(10, 10, 10, 10)
  ) +
  labs(
    title = "Correlation Between Immigration Attitudes and Demographics",
    subtitle = "Spearman's rank correlation coefficients",
    caption = "Note: Higher values indicate more positive attitudes toward immigration\nSample sizes shown in parentheses"
  )

```

```{r}
# 1. DATA PREPARATION 
df <- data %>%  
  mutate(
    immigrant_attitude = case_when(
      immigrant_numbers == "Government should significantly reduce the numbers"  ~ "Significantly reduce",
      immigrant_numbers == "Government should slightly reduce the numbers"  ~ "Slightly reduce",
      immigrant_numbers == "Government should keep the number the same"  ~ "Keep same",
      immigrant_numbers == "Government should slightly increase the numbers" ~ "Slightly increase",
      immigrant_numbers == "Government should significantly increase the numbers"  ~ "Significantly increase",
      TRUE ~ NA_character_
    ),
    
    # Keep categorical variables as factors with meaningful labels
    gender_clean = factor(gender),
    
    education_clean = case_when(
      degree == "No degree" ~ "No degree",
      degree == "Degree" ~ "Degree",
      TRUE ~ NA_character_
    ),
    
    urbanrural_clean = factor(urbanrural, levels = c("Rural Area", "Village", "Small Town", 
                                                     "Large Town", "Suburbs", "Urban/City Centre")),
    
    financial_clean = case_when(
      finances == "I cannot afford my costs and often have to go without essentials like food and heating" ~ "Cannot afford essentials",
      finances == "I can only just afford my costs and often struggle to make ends meet" ~ "Struggle to make ends meet",
      finances == "I do not have money for luxuries but can normally comfortably cover the essentials" ~ "Cover essentials only",
      finances == "I am relatively comfortable financially" ~ "Relatively comfortable",
      finances == "I am very comfortable financially" ~ "Very comfortable",
      TRUE ~ NA_character_
    ),
    
    voting_clean = case_when(
      votingintention_headline == "Reform UK" ~ "Reform UK",
      votingintention_headline == "Conservative" ~ "Conservative",
      votingintention_headline == "Liberal Democrat" ~ "Lib Dem",
      votingintention_headline == "Labour" ~ "Labour",
      votingintention_headline == "The Green Party" ~ "Green Party",
      TRUE ~ NA_character_
    )
  ) %>%
  # Order immigration attitudes
  mutate(immigrant_attitude = factor(immigrant_attitude, 
                                   levels = c("Significantly reduce", "Slightly reduce", "Keep same", 
                                            "Slightly increase", "Significantly increase")))

# 2. CREATE CROSS-TABULATION DATA 
create_crosstab_data <- function(demo_var, demo_name) {
  df %>%
    filter(!is.na(immigrant_attitude), !is.na(!!sym(demo_var))) %>%
    count(!!sym(demo_var), immigrant_attitude) %>%
    group_by(!!sym(demo_var)) %>%
    mutate(
      percentage = n / sum(n) * 100,
      demographic = demo_name,
      demo_level = as.character(!!sym(demo_var))
    ) %>%
    ungroup() %>%
    select(demographic, demo_level, immigrant_attitude, percentage)
}

# Combine all demographic variables
heatmap_data <- bind_rows(
  create_crosstab_data("gender_clean", "Gender"),
  create_crosstab_data("education_clean", "Education"),
  create_crosstab_data("urbanrural_clean", "Urban/Rural"),
  create_crosstab_data("financial_clean", "Financial Situation"),
  create_crosstab_data("voting_clean", "Voting Intention")
)

# 3. CREATE HEATMAP 
ggplot(heatmap_data, aes(x = immigrant_attitude, y = demo_level, fill = percentage)) +
  geom_tile(color = "white", size = 0.5) +
  geom_text(aes(label = paste0(round(percentage, 0), "%")), 
            color = "black", size = 3) +
  facet_wrap(~ demographic, scales = "free_y", ncol = 1) +
  scale_fill_gradient2(
    low = "white",
    high = "#2166ac",
    name = "Percentage"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(face = "bold", size = 10),
    legend.position = "right",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    panel.grid = element_blank()
  ) +
  labs(
    title = "Immigration Attitudes by Demographics",
    subtitle = "Percentage distribution within each demographic group",
    x = "Immigration Attitude",
    y = "Demographic Categories",
    caption = "Percentages show distribution within each demographic level"
  )

```



```{r}



# 1. DATA PREPARATION 
# Transform the wide format biggestissue columns to long format
issue_data <- data %>%
  # Select segment and all biggestissue columns
  select(segment, starts_with("biggestissue:")) %>%
  # Remove rows with missing segment
  filter(!is.na(segment)) %>%
  # Convert to long format
  pivot_longer(
    cols = starts_with("biggestissue:"),
    names_to = "issue_full",
    values_to = "selected"
  ) %>%
  # Clean up issue names by removing "biggestissue:" prefix
  mutate(
    issue = str_remove(issue_full, "biggestissue:"),
    selected = selected == "Selected"
  ) %>%
  # Filter to only selected issues
  filter(selected == TRUE) %>%
  # Clean up issue names for better display
  mutate(
    issue_clean = case_when(
      issue == "Affordable housing" ~ "Housing",
      issue == "Asylum seekers crossing the channel" ~ "Asylum seekers",
      issue == "Brexit" ~ "Brexit",
      issue == "Climate change and the environment" ~ "Climate/Environment",
      issue == "Levels of immigration" ~ "Immigration levels",
      issue == "Cost of living" ~ "Cost of living",
      issue == "Education and childcare" ~ "Education/Childcare",
      issue == "Crime" ~ "Crime",
      issue == "Social care for the elderly" ~ "Social care",
      issue == "Jobs and unemployment" ~ "Jobs/Unemployment",
      issue == "Mental health" ~ "Mental health",
      issue == "Conflict in the Middle East" ~ "Middle East conflict",
      issue == "The debate about transgender people" ~ "Transgender debate",
      issue == "Supporting the NHS" ~ "NHS",
      issue == "The war in Ukraine" ~ "Ukraine war",
      issue == "Welfare and benefits" ~ "Welfare/Benefits",
      issue == "Other (please specify)" ~ "Other",
      issue == "None of the above" ~ "None",
      TRUE ~ issue
    )
  )

# 2. CALCULATE PROPORTIONS BY SEGMENT 
segment_issue_props <- issue_data %>%
  # Count selections by segment and issue
  count(segment, issue_clean, name = "selections") %>%
  # Get total respondents per segment
  left_join(
    data %>% 
      filter(!is.na(segment)) %>%
      count(segment, name = "total_respondents"),
    by = "segment"
  ) %>%
  # Calculate proportion
  mutate(
    proportion = selections / total_respondents,
    percentage = proportion * 100
  ) %>%
  # Order segments logically
  mutate(
    segment = factor(segment, levels = c(
      "Progressive Activists", "Established Liberals", "Civic Pragmatists",
      "Disengaged Battlers", "Disengaged Traditionalists", 
      "Loyal Nationals", "Backbone Conservatives"
    ))
  )

```

```{r}

# 3. CREATE MOSAIC PLOT 
# For a true mosaic plot using ggmosaic
mosaic_plot <- segment_issue_props %>%
  ggplot() +
  geom_mosaic(aes(x = product(segment), fill = issue_clean, weight = selections)) +
  scale_fill_viridis_d(name = "Issue") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Issue Priorities by Political Segment",
    subtitle = "Mosaic plot showing proportion of each segment selecting each issue",
    x = "Political Segment",
    y = "Proportion",
    caption = "Note: Respondents could select up to 3 issues"
  )

print(mosaic_plot)

```

```{r}

# Alternative: Stacked bar chart (often easier to read than mosaic plots)
stacked_bar_plot <- segment_issue_props %>%
  ggplot(aes(x = segment, y = percentage, fill = issue_clean)) +
  geom_col(position = "stack") +
  scale_fill_viridis_d(name = "Issue") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Issue Priorities by Political Segment",
    subtitle = "Percentage of each segment selecting each issue (stacked)",
    x = "Political Segment",
    y = "Cumulative Percentage",
    caption = "Note: Respondents could select up to 3 issues, so totals exceed 100%"
  ) +
  coord_flip()

print(stacked_bar_plot)

```

```{r}

# 1. DATA PREPARATION #
# Transform the wide format biggestissue columns to long format
issue_data <- data %>%
  # Select segment and all biggestissue columns
  select(segment, starts_with("biggestissue:")) %>%
  # Remove rows with missing segment
  filter(!is.na(segment)) %>%
  # Convert to long format
  pivot_longer(
    cols = starts_with("biggestissue:"),
    names_to = "issue_full",
    values_to = "selected"
  ) %>%
  # Clean up issue names by removing "biggestissue:" prefix
  mutate(
    issue = str_remove(issue_full, "biggestissue:"),
    selected = selected == "Selected"
  ) %>%
  # Filter to only selected issues
  filter(selected == TRUE) %>%
  # Clean up issue names for better display (keep original categories)
  mutate(
    issue_clean = case_when(
      issue == "Affordable housing" ~ "Housing",
      issue == "Asylum seekers crossing the channel" ~ "Asylum seekers",
      issue == "Brexit" ~ "Brexit",
      issue == "Climate change and the environment" ~ "Climate/Environment",
      issue == "Levels of immigration" ~ "Immigration levels",
      issue == "Cost of living" ~ "Cost of living",
      issue == "Education and childcare" ~ "Education/Childcare",
      issue == "Crime" ~ "Crime",
      issue == "Social care for the elderly" ~ "Social care",
      issue == "Jobs and unemployment" ~ "Jobs/Unemployment",
      issue == "Mental health" ~ "Mental health",
      issue == "Conflict in the Middle East" ~ "Middle East conflict",
      issue == "The debate about transgender people" ~ "Transgender debate",
      issue == "Supporting the NHS" ~ "NHS",
      issue == "The war in Ukraine" ~ "Ukraine war",
      issue == "Welfare and benefits" ~ "Welfare/Benefits",
      TRUE ~ issue
    )
  ) %>%
  # Remove "Other" and "None" categories
  filter(!str_detect(issue, "Other|None"))

# 2. CALCULATE PROPORTIONS BY SEGMENT ------------------------------------
segment_issue_props <- issue_data %>%
  # Count selections by segment and issue
  count(segment, issue_clean, name = "selections") %>%
  # Get total respondents per segment
  left_join(
    data %>% 
      filter(!is.na(segment)) %>%
      count(segment, name = "total_respondents"),
    by = "segment"
  ) %>%
  # Calculate proportion
  mutate(
    proportion = selections / total_respondents,
    percentage = proportion * 100
  ) %>%
  # Order segments logically
  mutate(
    segment = factor(segment, levels = c(
      "Progressive Activists", "Established Liberals", "Civic Pragmatists",
      "Disengaged Battlers", "Disengaged Traditionalists", 
      "Loyal Nationals", "Backbone Conservatives"
    ))
  )

# 3. TOP 3 ISSUES PER SEGMENT --------------------------------------------
top3_by_segment <- segment_issue_props %>%
  group_by(segment) %>%
  slice_max(percentage, n = 3) %>%  # Get top 3 issues per segment
  mutate(
    rank = row_number(desc(percentage))
  ) %>%
  ungroup()

# 4. HORIZONTAL BAR CHART #
top3_bar_chart <- top3_by_segment %>%
  ggplot(aes(x = percentage, y = reorder_within(issue_clean, percentage, segment), fill = factor(rank))) +
  geom_col() +
  geom_text(aes(label = paste0(round(percentage, 0), "%")), 
            hjust = -0.1, size = 3) +
  scale_y_reordered() +
  scale_fill_manual(
    name = "Rank",
    values = c("1" = "#1f77b4", "2" = "#ff7f0e", "3" = "#2ca02c"),
    labels = c("1st", "2nd", "3rd")
  ) +
  facet_wrap(~ segment, scales = "free_y", ncol = 2) +
  theme_minimal() +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    axis.text.y = element_text(size = 8),
    legend.position = "none",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    # Remove gridlines - FIXED SYNTAX
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(
    title = "Top 3 Issue Priorities by Political Segment",
    subtitle = "Percentage of each segment selecting each issue",
    x = "",
    y = "Issue",
    caption = "Note: Respondents could select up to 3 issues"
  ) +
  xlim(0, max(top3_by_segment$percentage) * 1.2)  # Add space for labels

print(top3_bar_chart)




```

```{r}

top3_lollipop <- top3_by_segment %>%
  ggplot(aes(x = percentage, y = reorder_within(issue_clean, percentage, segment), color = factor(rank))) +
  geom_segment(aes(x = 0, xend = percentage, yend = reorder_within(issue_clean, percentage, segment)), 
               color = "grey50", size = 0.5) +
  geom_point(size = 3) +
  geom_text(aes(label = paste0(round(percentage, 0), "%")), 
            hjust = -0.3, size = 3) +
  scale_y_reordered() +
  scale_color_manual(
    values = c("1" = "#1f77b4", "2" = "#ff7f0e", "3" = "#2ca02c")
  ) +
  facet_wrap(~ segment, scales = "free_y", ncol = 2) +
  theme_minimal() +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    axis.text.y = element_text(size = 8),
    legend.position = "none",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    # Remove ALL gridlines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(
    title = "Top 3 Issue Priorities by Political Segment",
    subtitle = "Percentage of each segment selecting each issue",
    x = "",
    y = "Issue",
    caption = "Note: Respondents could select up to 3 issues"
  ) +
  xlim(0, max(top3_by_segment$percentage) * 1.2)

print(top3_lollipop)

```



```{r}

# 1. DATA PREPARATION 
# Prepare immigration position data
immigration_position <- data %>%
  filter(!is.na(segment), !is.na(immigrant_numbers), !is.na(UKNatRepWeight)) %>%
  # Collapse immigration position categories
  mutate(
    immigration_position = case_when(
      immigrant_numbers %in% c("Government should significantly increase the numbers", 
                              "Government should slightly increase the numbers") ~ "Increase",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the Same",
      immigrant_numbers %in% c("Government should significantly reduce the numbers",
                              "Government should slightly reduce the numbers") ~ "Decrease",
      TRUE ~ NA_character_
    )
  ) %>%
  # Remove "Don't know" responses
  filter(!is.na(immigration_position)) %>%
  # Create binary variable for immigration importance
  mutate(
    immigration_important = case_when(
      `biggestissue:Levels of immigration` == "Selected" ~ 1,
      `biggestissue:Levels of immigration` == "Not Selected" ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  # Remove missing values for immigration importance
  filter(!is.na(immigration_important))

# 2. CALCULATE WEIGHTED PERCENTAGES #
segment_immigration_summary <- immigration_position %>%
  group_by(segment, immigration_position) %>%
  summarise(
    # Weighted calculations
    total_weighted = sum(UKNatRepWeight),
    selected_weighted = sum(immigration_important * UKNatRepWeight),
    percentage_important = (selected_weighted / total_weighted) * 100,
    
    # Unweighted counts for reference
    total_unweighted = n(),
    selected_unweighted = sum(immigration_important),
    .groups = "drop"
  ) %>%
  # Order segments logically
  mutate(
    segment = factor(segment, levels = c(
      "Progressive Activists", "Civic Pragmatists", "Disengaged Battlers", 
       "Established Liberals", "Loyal Nationals", "Disengaged Traditionalists", 
       "Backbone Conservatives"
    )),
    # Order immigration positions logically
    immigration_position = factor(immigration_position, 
                                 levels = c("Decrease", "Keep the Same", "Increase"))
  )

# 3. CREATE BAR CHART #
immigration_bar_chart <- segment_immigration_summary %>%
  ggplot(aes(x = segment, y = percentage_important, fill = immigration_position)) +
  geom_col(position = "dodge", alpha = 0.8, width = 0.7) +
  geom_text(aes(label = ifelse(round(percentage_important, 0) == 0, 
                              "1%",
                              paste0(round(percentage_important, 0), "%"))), 
            position = position_dodge(width = 0.7), 
            vjust = -0.3, size = 3) +
  scale_fill_manual(
    name = "Immigration Position",
    values = c("Decrease" = "#d73027", "Keep the Same" = "#fee08b", "Increase" = "#4575b4")
  ) +
  scale_y_continuous(
    limits = c(0, 60),
    breaks = seq(0, 60, 10)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    panel.grid.major.x = element_blank(),
    # Remove ALL gridlines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(
    title = "Immigration Position Among Those Who Think It Is An Important Issue",
    subtitle = "",
    x = "Political Segment",
    y = "% Selecting Immigration as Important Issue",
    caption = "Note: Excludes 'Don't know' responses."
  )
print(immigration_bar_chart)


```

```{r}

## Immigration Position of those who don't consider it an important issue ##

# 1. DATA PREPARATION #
# Prepare immigration position data
immigration_position <- data %>%
  filter(!is.na(segment), !is.na(immigrant_numbers), !is.na(UKNatRepWeight)) %>%
  # Collapse immigration position categories
  mutate(
    immigration_position = case_when(
      immigrant_numbers %in% c("Government should significantly increase the numbers", 
                              "Government should slightly increase the numbers") ~ "Increase",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the Same",
      immigrant_numbers %in% c("Government should significantly reduce the numbers",
                              "Government should slightly reduce the numbers") ~ "Decrease",
      TRUE ~ NA_character_
    )
  ) %>%
  # Remove "Don't know" responses
  filter(!is.na(immigration_position)) %>%
  # Create binary variable for immigration NOT being important
  mutate(
    immigration_not_important = case_when(
      `biggestissue:Levels of immigration` == "Not Selected" ~ 1,
      `biggestissue:Levels of immigration` == "Selected" ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  # Remove missing values for immigration importance
  filter(!is.na(immigration_not_important))

# 2. CALCULATE WEIGHTED PERCENTAGES 
  group_by(segment, immigration_position) %>%
  summarise(
    # Weighted calculations
    total_weighted = sum(UKNatRepWeight),
    selected_weighted = sum(immigration_not_important * UKNatRepWeight),
    percentage_not_important = (selected_weighted / total_weighted) * 100,
    
    # Unweighted counts for reference
    total_unweighted = n(),
    selected_unweighted = sum(immigration_not_important),
    .groups = "drop"
  ) %>%
  # Order segments logically
  mutate(
    segment = factor(segment, levels = c(
      "Progressive Activists", "Civic Pragmatists", "Disengaged Battlers", 
       "Established Liberals", "Loyal Nationals", "Disengaged Traditionalists", 
       "Backbone Conservatives"
    )),
    # Order immigration positions logically
    immigration_position = factor(immigration_position, 
                                 levels = c("Decrease", "Keep the Same", "Increase"))
  )

# 3. CREATE BAR CHART 
immigration_bar_chart <- segment_immigration_summary %>%
  ggplot(aes(x = segment, y = percentage_not_important, fill = immigration_position)) +
  geom_col(position = "dodge", alpha = 0.8, width = 0.7) +
  geom_text(aes(label = ifelse(round(percentage_not_important, 0) == 0, 
                              "1%",
                              paste0(round(percentage_not_important, 0), "%"))), 
            position = position_dodge(width = 0.7), 
            vjust = -0.3, size = 3) +
  scale_fill_manual(
    name = "Immigration Position",
    values = c("Decrease" = "#d73027", "Keep the Same" = "#fee08b", "Increase" = "#4575b4")
  ) +
  scale_y_continuous(
    limits = c(0, 100),  # Added missing closing parenthesis here
    breaks = seq(0, 100, 20)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    # Remove ALL gridlines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(
    title = "Immigration Position Among those Who Don't Think It Is An Important Issue",
    subtitle = "",
    x = "Political Segment",
    y = "% NOT Selecting Immigration as Important Issue",
    caption = "Note: Excludes 'Don't know' responses."
  )  # Added missing closing parenthesis here
print(immigration_bar_chart)
# 4. SUMMARY TABLE 
print("Summary of weighted sample sizes by segment and position:")
print(segment_immigration_summary %>%
  select(segment, immigration_position, total_weighted, total_unweighted, percentage_not_important) %>%
  arrange(segment, immigration_position))

```

```{r}


# Prepare refugee position data
refugee_position <- data %>%
  filter(!is.na(segment), !is.na(refugees_numbers), !is.na(UKNatRepWeight)) %>%
  # Collapse refugee position categories
  mutate(
    refugee_position = case_when(
      refugees_numbers %in% c("Government should significantly increase the numbers", 
                              "Government should slightly increase the numbers") ~ "Increase Numbers",
      refugees_numbers == "Government should keep the number the same" ~ "Keep the Same",
      refugees_numbers %in% c("Government should significantly reduce the numbers",
                              "Government should slightly reduce the numbers") ~ "Reduce Numbers",
      TRUE ~ NA_character_
    )
  ) %>%
  # Remove "Don't know" responses
  filter(!is.na(refugee_position)) %>%
  # Create binary variable for asylum seekers importance
  mutate(
    asylum_important = case_when(
      `biggestissue:Asylum seekers crossing the channel` == "Selected" ~ 1,
      `biggestissue:Asylum seekers crossing the channel` == "Not Selected" ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  # Remove missing values for asylum importance
  filter(!is.na(asylum_important))

# 2. CALCULATE WEIGHTED PERCENTAGES 
segment_asylum_summary <- refugee_position %>%
  group_by(segment, refugee_position) %>%
  summarise(
    # Weighted calculations
    total_weighted = sum(UKNatRepWeight),
    selected_weighted = sum(asylum_important * UKNatRepWeight),
    percentage_important = (selected_weighted / total_weighted) * 100,
    
    # Unweighted counts for reference
    total_unweighted = n(),
    selected_unweighted = sum(asylum_important),
    .groups = "drop"
  ) %>%
  # Order segments logically
  mutate(
    segment = factor(segment, levels = c(
      "Progressive Activists", "Civic Pragmatists", 
      "Disengaged Battlers", "Established Liberals", "Loyal Nationals",
      "Disengaged Traditionalists", "Backbone Conservatives"
    )),
    # Order refugee positions logically
    refugee_position = factor(refugee_position, 
                             levels = c("Reduce Numbers", "Keep the Same", "Increase Numbers"))
  )

# 3. CREATE BAR CHART 
asylum_bar_chart <- segment_asylum_summary %>%
  ggplot(aes(x = segment, y = percentage_important, fill = refugee_position)) +
  geom_col(position = "dodge", alpha = 0.8, width = 0.7) +
  geom_text(aes(label = ifelse(round(percentage_important, 0) == 0, 
                              "1%",
                              paste0(round(percentage_important, 0), "%"))), 
            position = position_dodge(width = 0.7), 
            vjust = -0.3, size = 3) +
  scale_fill_manual(
    name = "Refugee Policy Position",
    values = c("Reduce Numbers" = "#d73027", "Keep the Same" = "#fee08b", "Increase Numbers" = "#4575b4")
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    # Remove ALL gridlines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +

  labs(
    title = "Asylum Position Among those Who Think It is An Important Issue",
    subtitle = "",
    x = "Political Segment",
    y = "% Selecting Asylum Seekers as Important Issue",
    caption = "Note: Excludes 'Don't know' responses."
) +
ylim(0, max(segment_asylum_summary$percentage_important) * 1.1)
print(asylum_bar_chart)

# 4. SUMMARY TABLE #
print("Summary of weighted sample sizes by segment and position:")
print(segment_asylum_summary %>%
  select(segment, refugee_position, total_weighted, total_unweighted, percentage_important) %>%
  arrange(segment, refugee_position))

```

```{r}

## asylum attitudes among those not important ## 
# 1. DATA PREPARATION 
# Prepare refugee position data
refugee_position <- data %>%
  filter(!is.na(segment), !is.na(refugees_numbers), !is.na(UKNatRepWeight)) %>%
  # Collapse refugee position categories
  mutate(
    refugee_position = case_when(
      refugees_numbers %in% c("Government should significantly increase the numbers", 
                              "Government should slightly increase the numbers") ~ "Increase Numbers",
      refugees_numbers == "Government should keep the number the same" ~ "Keep the Same",
      refugees_numbers %in% c("Government should significantly reduce the numbers",
                              "Government should slightly reduce the numbers") ~ "Reduce Numbers",
      TRUE ~ NA_character_
    )
  ) %>%
  # Remove "Don't know" responses
  filter(!is.na(refugee_position)) %>%
  # Create binary variable for asylum seekers NOT being important
  mutate(
    asylum_not_important = case_when(
      `biggestissue:Asylum seekers crossing the channel` == "Not Selected" ~ 1,
      `biggestissue:Asylum seekers crossing the channel` == "Selected" ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  # Remove missing values for asylum importance
  filter(!is.na(asylum_not_important))

# 2. CALCULATE WEIGHTED PERCENTAGES
segment_asylum_summary <- refugee_position %>%
  group_by(segment, refugee_position) %>%
  summarise(
    # Weighted calculations
    total_weighted = sum(UKNatRepWeight),
    selected_weighted = sum(asylum_not_important * UKNatRepWeight),
    percentage_not_important = (selected_weighted / total_weighted) * 100,
    
    # Unweighted counts for reference
    total_unweighted = n(),
    selected_unweighted = sum(asylum_not_important),
    .groups = "drop"
  ) %>%
  # Order segments logically
  mutate(
    segment = factor(segment, levels = c(
      "Progressive Activists", "Civic Pragmatists", 
      "Disengaged Battlers", "Established Liberals", "Loyal Nationals",
      "Disengaged Traditionalists", "Backbone Conservatives"
    )),
    # Order refugee positions logically
    refugee_position = factor(refugee_position, 
                             levels = c("Reduce Numbers", "Keep the Same", "Increase Numbers"))
  )

# 3. CREATE BAR CHART
asylum_bar_chart <- segment_asylum_summary %>%
  ggplot(aes(x = segment, y = percentage_not_important, fill = refugee_position)) +
  geom_col(position = "dodge", alpha = 0.8, width = 0.7) +
  geom_text(aes(label = ifelse(round(percentage_not_important, 0) == 0, 
                              "1%",
                              paste0(round(percentage_not_important, 0), "%"))), 
            position = position_dodge(width = 0.7), 
            vjust = -0.3, size = 3) +
  scale_fill_manual(
    name = "Refugee Policy Position",
    values = c("Reduce Numbers" = "#d73027", "Keep the Same" = "#fee08b", "Increase Numbers" = "#4575b4")
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    legend.position = "bottom",
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    # Remove ALL gridlines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(
    title = "Asylum Position Among those Who Don't Think It is An Important Issue",
    subtitle = "",
    x = "Political Segment",
    y = "% NOT Selecting Asylum Seekers as Important Issue",
    caption = "Note: Excludes 'Don't know' responses."
  ) +
  ylim(0, max(segment_asylum_summary$percentage_not_important) * 1.1)

print(asylum_bar_chart)

# 4. SUMMARY TABLE
print("Summary of weighted sample sizes by segment and position:")
print(segment_asylum_summary %>%
  select(segment, refugee_position, total_weighted, total_unweighted, percentage_not_important) %>%
  arrange(segment, refugee_position))






```

```{r}


# Aggregate across all segments for cleaner comparison
overall_comparison <- immigration_position %>%
  group_by(immigration_position) %>%
  summarise(
    total_weighted = sum(UKNatRepWeight),
    selected_weighted = sum(immigration_important * UKNatRepWeight),
    percentage_important = (selected_weighted / total_weighted) * 100,
    .groups = "drop"
  )

simple_bar_chart <- overall_comparison %>%
  ggplot(aes(x = immigration_position, y = percentage_important, fill = immigration_position)) +
  geom_col(alpha = 0.8, width = 0.6) +
  geom_text(aes(label = paste0(round(percentage_important, 0), "%")), 
            vjust = -0.3, size = 4, fontweight = "bold") +
  scale_fill_manual(values = c("Decrease" = "#d73027", "Keep the Same" = "#fee08b", "Increase" = "#4575b4")) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.text.x = element_text(size = 11)
  ) +
  labs(
    title = "Immigration Salience by Policy Position",
    subtitle = "Percentage considering immigration a top priority",
    x = "Immigration Policy Preference",
    y = "% Selecting Immigration as Important Issue"
  )

print(simple_bar_chart)





```

```{r}
library(tidyverse)
library(scales)

# Prepare the data with three categories
slope_data <- data %>%
  mutate(
    immigration_attitude = case_when(
      str_detect(immigrant_numbers, "Government should significantly increase the numbers|Government should slightly increase the numbers") ~ "Increase numbers",
      str_detect(immigrant_numbers, "Government should keep the number the same") ~ "Keep the same",
      str_detect(immigrant_numbers, "Government should significantly reduce the numbers|Government should slightly reduce the numbers") ~ "Reduce numbers",
      TRUE ~ "Don't know"
    )
  ) %>%
  filter(immigration_attitude != "Don't know")  # Remove "Don't know" if desired

# For each immigration attitude, calculate the proportion who consider immigration important
plot_data <- slope_data %>%
  group_by(immigration_attitude) %>%
  summarise(
    total = n(),
    important = sum(`biggestissue:Levels of immigration` == "Selected"),
    prop_important = important / total
  ) %>%
  mutate(
    immigration_attitude = factor(
      immigration_attitude,
      levels = c("Increase numbers", "Keep the same", "Reduce numbers")
    )
  ) %>%
  arrange(immigration_attitude)

# Plot: dot and line connecting proportions
ggplot(plot_data, aes(x = immigration_attitude, y = prop_important, group = 1)) +
  geom_line(color = "blue", linewidth = 1) +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = scales::percent(prop_important, accuracy = 1)), vjust = -1, size = 4) +
  labs(
    title = "Proportion Who Consider Immigration Important by Immigration Policy Position",
    x = "Immigration Policy Position",
    y = "Proportion Who Consider Immigration Important"
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 0.5), breaks = seq(0, 0.5, 0.1)) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

```


```{r}
#For each policy position, what percentage say immigration is important?

## For each immigration policy position, calculate the proportion of people who say immigration is important (i.e., "Selected" for biggestissue:Levels of immigration),

#The denominator is everyone with that policy position.

# 1. Recode immigration policy positions (exact matching)
policy_data <- data %>%
  mutate(
    immigration_attitude = case_when(
      immigrant_numbers == "Government should significantly increase the numbers" ~ "Significantly Increase",
      immigrant_numbers == "Government should slightly increase the numbers" ~ "Slightly Increase",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the same",
      immigrant_numbers == "Government should slightly reduce the numbers" ~ "Slightly Reduce",
      immigrant_numbers == "Government should significantly reduce the numbers" ~ "Significantly Reduce",
      TRUE ~ "Don't know"
    )
  ) %>%
  filter(immigration_attitude != "Don't know")

# 2. Calculate, for each policy position, the proportion who say immigration is important
plot_data <- policy_data %>%
  group_by(immigration_attitude) %>%
  summarise(
    total = n(),
    important = sum(`biggestissue:Levels of immigration` == "Selected"),
    prop_important = important / total
  ) %>%
  mutate(
    immigration_attitude = factor(
      immigration_attitude,
      levels = c("Significantly Increase", "Slightly Increase",
                 "Keep the same", "Slightly Reduce", "Significantly Reduce")
    )
  ) %>%
  arrange(immigration_attitude)

# 3. Plot
library(ggplot2)
ggplot(plot_data, aes(x = immigration_attitude, y = prop_important, group = 1)) +
  geom_line(color = "blue", linewidth = 1) +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = scales::percent(prop_important, accuracy = 1)), vjust = -1, size = 4) +
  labs(
    title = "Proportion Who Consider Immigration Important by Immigration Policy Position",
    x = "Immigration Policy Position",
    y = "Proportion Who Consider Immigration Important"
  ) +
  scale_y_continuous(
    limits = c(0, 0.6),
    breaks = seq(0, 0.6, 0.1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

print(plot_data)




```





```{r}

slope_data <- data %>%
  mutate(
    immigration_attitude = case_when(
      str_detect(immigrant_numbers, "Government should significantly increase the numbers") ~ "Significantly Increase",
      str_detect(immigrant_numbers, "Government should slightly increase the numbers") ~ "Slightly Increase",
      str_detect(immigrant_numbers, "Government should keep the number the same") ~ "Keep the same",
      str_detect(immigrant_numbers, "Government should slightly reduce the numbers") ~ "Slightly Reduce",
      str_detect(immigrant_numbers, "Government should significantly reduce the numbers") ~ "Significantly Reduce",
      TRUE ~ "Don't know"
    )
  ) %>%
  filter(immigration_attitude != "Don't know")  # Remove "Don't know" if desired

# 2. Calculate proportions
plot_data <- slope_data %>%
  group_by(immigration_attitude) %>%
  summarise(
    total = n(),
    important = sum(`biggestissue:Levels of immigration` == "Selected"),
    prop_important = important / total
  ) %>%
  mutate(
    immigration_attitude = factor(
      immigration_attitude,
      levels = c("Significantly Increase", "Slightly Increase",
                 "Keep the same", "Slightly Reduce", "Significantly Reduce")
    )
  ) %>%
  arrange(immigration_attitude)

# 3. Plot with tilted x-axis labels
ggplot(plot_data, aes(x = immigration_attitude, y = prop_important, group = 1)) +
  geom_line(color = "blue", linewidth = 1) +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = scales::percent(prop_important, accuracy = 1)), vjust = -1, size = 4) +
  labs(
    title = "By Policy Position What Proportion Think Immigration Is Imoportant",
    x = "Immigration Policy Position",
    y = "Proportion Who Consider Immigration Important"
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 0.5), breaks = seq(0, 0.5, 0.1)) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



```


```{r}

# 1. Filter to only those who say immigration is important and recode policy position
important_data <- data %>%
  filter(`biggestissue:Levels of immigration` == "Selected") %>%
  mutate(
    immigration_attitude = case_when(
      immigrant_numbers == "Government should significantly increase the numbers" ~ "Significantly Increase",
      immigrant_numbers == "Government should slightly increase the numbers" ~ "Slightly Increase",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the same",
      immigrant_numbers == "Government should slightly reduce the numbers" ~ "Slightly Reduce",
      immigrant_numbers == "Government should significantly reduce the numbers" ~ "Significantly Reduce",
      TRUE ~ "Don't know"
    )
  ) %>%
  filter(immigration_attitude != "Don't know")

# 2. Check that all categories are present
print(table(important_data$immigration_attitude))

# 3. Calculate proportions within the "important" group
plot_data <- important_data %>%
  group_by(immigration_attitude) %>%
  summarise(n = n()) %>%
  mutate(
    prop = n / sum(n),
    immigration_attitude = factor(
      immigration_attitude,
      levels = c("Significantly Increase", "Slightly Increase",
                 "Keep the same", "Slightly Reduce", "Significantly Reduce")
    )
  ) %>%
  arrange(immigration_attitude)

# 4. Plot
library(ggplot2)
ggplot(plot_data, aes(x = immigration_attitude, y = prop, group = 1)) +
  geom_line(color = "blue", linewidth = 1) +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = scales::percent(prop, accuracy = 1)), vjust = -1, size = 4) +
  labs(
    title = "Policy Position Breakdown Among Those Who Consider Immigration Important",
    x = "Immigration Policy Position",
    y = "Proportion of 'Important' Group"
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
    
  )
```

```{r}

diverging_data <- overall_comparison %>%
  mutate(
    # Center around "Keep Same" position
    baseline = overall_comparison$percentage_important[overall_comparison$immigration_position == "Keep the Same"],
    difference = percentage_important - baseline,
    direction = ifelse(difference > 0, "Higher than baseline", "Lower than baseline")
  )

diverging_chart <- diverging_data %>%
  ggplot(aes(x = immigration_position, y = difference, fill = direction)) +
  geom_col(alpha = 0.8, width = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_text(aes(label = paste0(ifelse(difference > 0, "+", ""), round(difference, 1), "pp")), 
            vjust = ifelse(diverging_data$difference > 0, -0.3, 1.3), size = 4) +
  scale_fill_manual(values = c("Higher than baseline" = "#d73027", "Lower than baseline" = "#4575b4")) +
  theme_minimal() +
  labs(
    title = "Immigration Salience Relative to 'Keep Same' Position",
    subtitle = "Difference in percentage points from baseline",
    x = "Immigration Policy Position",
    y = "Difference from 'Keep Same' baseline (percentage points)"
  )

print(diverging_chart)

```


```{r}
# FIXED: Corrected factor levels to match exactly with the data and color mapping
attitude_levels <- c("Significantly Reduce", "Slightly Reduce", "Keep the Same", "Don't know", "Slightly Increase", "Significantly Increase")

# --- IMMIGRATION PLOT ---

crime_immigration_data <- data %>%
  filter(!is.na(UKNatRepWeight), !is.na(`biggestissue:Crime`), !is.na(immigrant_numbers)) %>%
  mutate(
    crime_selected = case_when(
      `biggestissue:Crime` == "Selected" ~ "Selected Crime as Important",
      `biggestissue:Crime` == "Not Selected" ~ "Did Not Select Crime",
      TRUE ~ NA_character_
    ),
    immigration_attitude = case_when(
      is.na(immigrant_numbers) ~ "Don't know",
      immigrant_numbers == "Government should significantly increase the numbers" ~ "Significantly Increase",
      immigrant_numbers == "Government should slightly increase the numbers" ~ "Slightly Increase",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the Same",
      immigrant_numbers == "Government should significantly reduce the numbers" ~ "Significantly Reduce",
      immigrant_numbers == "Government should slightly reduce the numbers" ~ "Slightly Reduce",
      immigrant_numbers == "Don't know" ~ "Don't know",
      TRUE ~ "Don't know"
    )
  ) %>%
  filter(!is.na(crime_selected), !is.na(immigration_attitude))

plot_data_immigration_crime <- crime_immigration_data %>%
  group_by(crime_selected, immigration_attitude) %>%
  summarise(weighted_n = sum(UKNatRepWeight, na.rm = TRUE), .groups = "drop") %>%
  group_by(crime_selected) %>%
  mutate(
    total_weighted = sum(weighted_n),
    percentage = (weighted_n / total_weighted) * 100
  ) %>%
  ungroup()

# Set factor levels immediately before plotting
plot_data_immigration_crime$immigration_attitude <- factor(
  plot_data_immigration_crime$immigration_attitude,
  levels = attitude_levels
)

crime_immigration_plot_horizontal <- 
  ggplot(plot_data_immigration_crime, 
    aes(x = crime_selected, y = percentage, fill = immigration_attitude)) +
  geom_col(position = "stack", alpha = 0.8) +
  geom_text(aes(label = ifelse(percentage >= 1, paste0(round(percentage, 0), "%"), "")), 
            position = position_stack(vjust = 0.5), 
            size = 3.5, 
            color = "white", 
            fontface = "bold") +
  scale_fill_manual(
    values = c(
      "Significantly Increase" = "#D53E4F",
      "Slightly Increase" = "#FC8D59",
      "Keep the Same" = "#fee08b",
      "Don't know" = "grey60",
      "Slightly Reduce" = "#99D594",
      "Significantly Reduce" = "#3288BD"
    ),
    name = "Immigration\nAttitude",
    drop = FALSE
  ) +
  labs(
    title = "Immigration Attitudes by Crime Issue Priority",
    subtitle = "",
    x = "",  # FIXED: Correct axis label
    y = "",              # FIXED: Correct axis label
    caption = ""
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 12, face = "bold"),
    legend.position = "right",
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 11),
    panel.grid = element_blank()
  ) +
  coord_flip() +
  ylim(0, 100.1)

# --- REFUGEES PLOT ---

crime_refugees_data <- data %>%
  filter(!is.na(UKNatRepWeight), !is.na(`biggestissue:Welfare and benefits`), !is.na(refugees_numbers)) %>%
  mutate(
    crime_selected = case_when(
      `biggestissue:Crime` == "Selected" ~ "Selected Welfare as Important",
      `biggestissue:Crime` == "Not Selected" ~ "Did Not Select Welfare",
      TRUE ~ NA_character_
    ),
    refugees_attitude = case_when(
      is.na(refugees_numbers) ~ "Don't know",
      refugees_numbers == "Government should significantly increase the numbers" ~ "Significantly Increase",
      refugees_numbers == "Government should slightly increase the numbers" ~ "Slightly Increase",
      refugees_numbers == "Government should keep the number the same" ~ "Keep the Same",
      refugees_numbers == "Government should significantly reduce the numbers" ~ "Significantly Reduce",
      refugees_numbers == "Government should slightly reduce the numbers" ~ "Slightly Reduce",
      refugees_numbers == "Don't know" ~ "Don't know",
      TRUE ~ "Don't know"
    )
  ) %>%
  filter(!is.na(crime_selected), !is.na(refugees_attitude))

plot_data_refugees_crime <- crime_refugees_data %>%
  group_by(crime_selected, refugees_attitude) %>%
  summarise(weighted_n = sum(UKNatRepWeight, na.rm = TRUE), .groups = "drop") %>%
  group_by(crime_selected) %>%
  mutate(
    total_weighted = sum(weighted_n),
    percentage = (weighted_n / total_weighted) * 100
  ) %>%
  ungroup()

# Set factor levels immediately before plotting
plot_data_refugees_crime$refugees_attitude <- factor(
  plot_data_refugees_crime$refugees_attitude,
  levels = attitude_levels
)

crime_refugee_plot_horizontal <- 
  ggplot(plot_data_refugees_crime, 
    aes(x = crime_selected, y = percentage, fill = refugees_attitude)) +
  geom_col(position = "stack", alpha = 0.8) +
  geom_text(aes(label = ifelse(percentage >= 1, paste0(round(percentage, 0), "%"), "")), 
            position = position_stack(vjust = 0.5), 
            size = 3.5, 
            color = "white", 
            fontface = "bold") +
  scale_fill_manual(
    values = c(
      "Significantly Increase" = "#D53E4F",
      "Slightly Increase" = "#FC8D59",
      "Keep the Same" = "#fee08b",
      "Don't know" = "grey60",
      "Slightly Reduce" = "#99D594",
      "Significantly Reduce" = "#3288BD"
    ),
    name = "Refugees\nAttitude",
    drop = FALSE
  ) +
  labs(
    title = "Refugee Attitudes by Crime Issue Priority",
    subtitle = "",
    x = "",  # FIXED: Correct axis label
    y = "",              # FIXED: Correct axis label
    caption = ""
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    strip.text = element_text(size = 12, face = "bold"),
    legend.position = "right",
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 11),
    panel.grid = element_blank()
  ) +
  coord_flip() +
  ylim(0, 100.1)

# --- Combine plots vertically ---
combined_plot_crime <- crime_immigration_plot_horizontal / crime_refugee_plot_horizontal

print(combined_plot_crime)




```


```{r}
## Overall immigration and refugee attitudes
data_overall <- data %>%
  mutate(
    immigrant_numbers = str_replace_all(immigrant_numbers, "'", "'"),
    refugees_numbers = str_replace_all(refugees_numbers, "'", "'"),
    immigrant_numbers = str_trim(immigrant_numbers),
    refugees_numbers = str_trim(refugees_numbers),
    # Additional cleaning for "Don't know" variations
    immigrant_numbers = case_when(
      str_detect(immigrant_numbers, "Don.t know") ~ "Don't know",
      TRUE ~ immigrant_numbers
    ),
    refugees_numbers = case_when(
      str_detect(refugees_numbers, "Don.t know") ~ "Don't know",
      TRUE ~ refugees_numbers
    )
  )

# Define category order and labels
attitude_levels <- c(
  "Government should significantly increase the numbers",
  "Government should slightly increase the numbers",
  "Government should keep the number the same",
  "Don't know",  # Use curly apostrophe to match data
  "Government should slightly reduce the numbers",
  "Government should significantly reduce the numbers"
)

attitude_labels <- c(
  "Significantly Increase",
  "Slightly Increase",
  "Keep the Same",
  "Don't know",  # Fixed: Use curly apostrophe consistently
  "Slightly Reduce",
  "Significantly Reduce"
)

attitude_colors <- c(
  "Significantly Increase" = "#D53E4F",
  "Slightly Increase" = "#FC8D59",
  "Keep the Same" = "#fee08b",
  "Don't know" = "grey60",  # Fixed: Use curly apostrophe consistently
  "Slightly Reduce" = "#99D594",
  "Significantly Reduce" = "#3288BD"
)

# Helper function to prep data for plotting
prep_attitude <- function(data_input, var, weight, levels, labels) {
  data_input %>%  # Fixed: Use the correct parameter name
    mutate(
      att = factor(.data[[var]], levels = levels, labels = labels)
    ) %>%
    count(att, wt = .data[[weight]], name = "weighted_n", drop = FALSE) %>%
    mutate(
      pct = weighted_n / sum(weighted_n, na.rm = TRUE),
      pct_label = percent(pct, accuracy = 1)
    )
}

# Immigration attitudes
immigration_data <- prep_attitude(data_overall, "immigrant_numbers", "UKNatRepWeight", attitude_levels, attitude_labels)

# Refugee attitudes
refugee_data <- prep_attitude(data_overall, "refugees_numbers", "UKNatRepWeight", attitude_levels, attitude_labels)

# Immigration plot
p1 <- ggplot(immigration_data, aes(x = 1, y = pct, fill = att)) +
  geom_bar(stat = "identity", width = 0.25, position = position_stack(reverse = TRUE)) +  # Reduced width
  geom_text(aes(label = pct_label), 
            position = position_stack(vjust = 0.5, reverse = TRUE), 
            size = 3, color = "white") +  # Reduced text size
  scale_fill_manual(values = attitude_colors, name = "Attitude", drop = FALSE) +
  coord_flip() +
  labs(title = "Attitudes to Immigration", x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    plot.margin = margin(10, 10, 10, 10)  # Reduced margins
  )

# Refugee plot
p2 <- ggplot(refugee_data, aes(x = 1, y = pct, fill = att)) +
  geom_bar(stat = "identity", width = 0.25, position = position_stack(reverse = TRUE)) +  # Reduced width
  geom_text(aes(label = pct_label), 
            position = position_stack(vjust = 0.5, reverse = TRUE), 
            size = 3, color = "white") +  # Reduced text size
  scale_fill_manual(values = attitude_colors, name = "Attitude", drop = FALSE) +
  coord_flip() +
  labs(title = "Attitudes to Refugees", x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    plot.margin = margin(10, 10, 10, 10)  # Reduced margins
  )

# Combine with patchwork - with height control
combined_plot <- p1 / p2 + 
  plot_layout(guides = "collect", heights = c(1, 1))

# Display with controlled size
combined_plot
```


```{r}



library(dplyr)
library(ggplot2)

data <- read_csv(here("data", "immigration.csv"))

# Step 1: Recode to ALL categories using the EXACT strings from data
data <- data %>%
  mutate(
    immig_3cat = case_when(
      immigrant_numbers %in% c(
        "Government should significantly increase the numbers",
        "Government should slightly increase the numbers"
      ) ~ "Increase Numbers",
      immigrant_numbers %in% c(
        "Government should significantly reduce the numbers",
        "Government should slightly reduce the numbers"
      ) ~ "Reduce Numbers",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the Same",
      immigrant_numbers == "Don't know" ~ "Don't Know",
      TRUE ~ "Other"
    )
  )

# Step 2: Check data before filtering

# table(data$votingintention_headline, useNA = "always")
# table(data$immig_3cat, useNA = "always")
# table(data$votingintention_headline, data$immig_3cat, useNA = "always")

# Step 3: Define excluded parties (fix the "NA" issue)
excluded_parties <- c("Scottish National Party (SNP)", "Plaid Cymru", "Another party/Independent Candidate")

# Step 4: Prepare data for plotting - calculate percentages including ALL responses, then filter for display
plot_data <- data %>%
  # Remove excluded parties and handle NAs, but KEEP "Keep the Same" and "Don't Know"
  filter(
    !is.na(votingintention_headline),           
    !votingintention_headline %in% excluded_parties,
    votingintention_headline != "NA",           
    votingintention_headline != "",             
    immig_3cat %in% c("Increase Numbers", "Reduce Numbers", "Keep the Same", "Don't Know")  # Include all for calculation
  ) %>%
  # Count ALL responses by party and response type
  group_by(votingintention_headline, immig_3cat) %>%
  summarise(n = n(), .groups = "drop") %>%
  # Calculate total respondents per party (including Keep Same/Don't Know)
  group_by(votingintention_headline) %>%
  mutate(
    total_party_respondents = sum(n),
    percent = n / total_party_respondents * 100
  ) %>%
  ungroup() %>%
  # NOW filter to show only Increase/Reduce for plotting
  filter(immig_3cat %in% c("Increase Numbers", "Reduce Numbers")) %>%
  # Create the plotting variable
  mutate(
    immig_3cat = factor(immig_3cat, levels = c("Reduce Numbers", "Increase Numbers")),
    percent_plot = if_else(immig_3cat == "Reduce Numbers", -percent, percent)
  )

# Step 5: DIAGNOSTIC - Check  processed data
print("Summary of plot_data:")
print(plot_data)
print("\nParty response counts:")
print(plot_data %>% group_by(votingintention_headline) %>% summarise(total = sum(n)))

# Step 6: Create the plot
p <- ggplot(plot_data, aes(x = reorder(votingintention_headline, percent_plot), 
                          y = percent_plot, fill = immig_3cat)) +
  geom_col(width = 0.7, position = "identity") +  # Added position = "identity"
  coord_flip() +
  scale_fill_manual(
    values = c("Reduce Numbers" = "#d73027", "Increase Numbers" = "#4575b4"),
    name = "Immigration Attitude"
  ) +
  scale_y_continuous(
    labels = function(x) paste0(abs(x)),  # Better label formatting
    name = "Percent",  # Remove the axis title here
    breaks = seq(-100, 60, by = 20),  # Adjusted breaks for new range
    limits = c(-100, 60)  # Changed to accommodate high "Reduce" percentages
  ) +
  labs(
    title = "Divisions Within Parties on Immigration Policy",
    x = "Vote Intention",
    y = "Percent of Respondents",
    caption = "Percentages calculated from all party respondents. Figures in the graph Do not add up to 100% because 'Keep the same' and 'Don't know' are not displayed"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    panel.grid.major = element_blank(),  # Remove ALL major grid lines
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 10)
  ) +
  # Add a vertical line at zero
  geom_vline(xintercept = 0, color = "black", size = 0.3)

# Display the plot
print(p)

# Step 7: Additional diagnostics - run these to troubleshoot
cat("\n=== DIAGNOSTIC INFORMATION ===\n")
cat("Unique parties in original data:\n")
print(unique(data$votingintention_headline))
cat("\nUnique immigration responses in original data:\n")
print(unique(data$immigrant_numbers))
cat("\nNA values in key variables:\n")
cat("votingintention_headline NAs:", sum(is.na(data$votingintention_headline)), "\n")
cat("immigrant_numbers NAs:", sum(is.na(data$immigrant_numbers)), "\n")
cat("immig_3cat NAs:", sum(is.na(data$immig_3cat)), "\n")


```

```{r}


#  Recode to two categories, excluding 'Keep the same' and 'Don't know'
data <- data %>%
  mutate(
    immig_3cat = case_when(
      immigrant_numbers %in% c(
        "Government should significantly increase the numbers",
        "Government should slightly increase the numbers"
      ) ~ "Increase",
      immigrant_numbers %in% c(
        "Government should slightly reduce the numbers",
        "Government should significantly reduce the numbers"
      ) ~ "Reduce",
      TRUE ~ NA_character_
    )
  )

# Step 2: Check  data before filtering

# table(data$votingintention_headline, useNA = "always")
# table(data$immig_3cat, useNA = "always")
# table(data$votingintention_headline, data$immig_3cat, useNA = "always")

# Step 3: Define excluded parties (fix the "NA" issue)
excluded_parties <- c("Scottish National Party (SNP)", "Plaid Cymru", "Another party/Independent Candidate")

# Step 4: Prepare data for plotting with better filtering
plot_data <- data %>%
  # Remove NAs and excluded parties more carefully
  filter(
    !is.na(immig_3cat),
    !is.na(votingintention_headline),
    !votingintention_headline %in% excluded_parties,
    votingintention_headline != "NA",  # Handle "NA" as string separately
    votingintention_headline != ""     # Handle empty strings
  ) %>%
  # Group and calculate percentages
  group_by(votingintention_headline, immig_3cat) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(votingintention_headline) %>%
  mutate(
    total_responses = sum(n),
    percent = n / sum(n) * 100
  ) %>%
  ungroup() %>%
  # Create the plotting variable
  mutate(
    immig_3cat = factor(immig_3cat, levels = c("Reduce", "Increase")),
    percent_plot = if_else(immig_3cat == "Reduce", -percent, percent)
  )

# Step 5: DIAGNOSTIC - 
print("Summary of plot_data:")
print(plot_data)
print("\nParty response counts:")
print(plot_data %>% group_by(votingintention_headline) %>% summarise(total = sum(n)))

# Step 6: Create the plot
p <- ggplot(plot_data, aes(x = reorder(votingintention_headline, percent_plot), 
                          y = percent_plot, fill = immig_3cat)) +
  geom_col(width = 0.7, position = "identity") +  # Added position = "identity"
  coord_flip() +
  scale_fill_manual(
    values = c("Reduce" = "#d73027", "Increase" = "#4575b4"),
    name = "Immigration Attitude"
  ) +
  scale_y_continuous(
    labels = function(x) paste0(abs(x), "%"),  # Better label formatting
    name = "Percent of respondents",
    breaks = seq(-90, 50, by = 20),
    limits = c(-90, 50)
  ) +
  labs(
    title = "Partisan Polarization on Immigration Numbers",
    x = "Vote Intention",
    y = "Percent of Respondents"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_blank(),  # Keep horizontal grid lines
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 10)
  ) +
  # Add a vertical line at zero
  geom_vline(xintercept = 0, color = "black", size = 0.3)

# Display the plot
print(p)

# Step 7: Additional diagnostics -
cat("\n=== DIAGNOSTIC INFORMATION ===\n")
cat("Unique parties in original data:\n")
print(unique(data$votingintention_headline))
cat("\nUnique immigration responses in original data:\n")
print(unique(data$immigrant_numbers))
cat("\nNA values in key variables:\n")
cat("votingintention_headline NAs:", sum(is.na(data$votingintention_headline)), "\n")
cat("immigrant_numbers NAs:", sum(is.na(data$immigrant_numbers)), "\n")
cat("immig_3cat NAs:", sum(is.na(data$immig_3cat)), "\n")

```



```{r} 
library(dplyr)
library(ggplot2)
library(scales)

# Set  color mapping ##
interest_colors <- c(
  "Hardly interested" = "#D53E4F",
  "Not interested at all" = "#fee08b",
  "Quite interested" = "#99D594",
  "Very interested" = "#3288BD"
)




# Collapse immigrant_numbers into three categories
df <- data %>%
  mutate(
    migration_pref = case_when(
      immigrant_numbers %in% c(
        "Government should significantly increase the numbers",
        "Government should slightly increase the numbers"
      ) ~ "Increase",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the same",
      immigrant_numbers %in% c(
        "Government should slightly reduce the numbers",
        "Government should significantly reduce the numbers"
      ) ~ "Reduce",
      TRUE ~ NA_character_
    ),
    migration_pref = factor(migration_pref, levels = c("Increase", "Keep the same", "Reduce"))
  )

# Calculate percentages WITHIN each migration preference group
plot_data <- df %>%
  filter(!is.na(migration_pref), !is.na(political_interest)) %>%
  group_by(migration_pref, political_interest) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(migration_pref) %>%
  mutate(
    pct = n / sum(n)
  ) %>%
  ungroup()

# Plot
ggplot(plot_data, aes(x = migration_pref, y = pct, fill = political_interest)) +
  geom_col(position = "fill") +
  geom_text(
    aes(label = percent(pct, accuracy = 1)),
    position = position_fill(vjust = 0.5),
    color = "white",
    size = 3.5
  ) +
  scale_fill_manual(values = interest_colors, name = "Political Interest") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    x = "Migration Preference",
    y = "Percentage of Respondents",
    fill = "Political Interest",
    title = "Political Interest Distribution Within Each Migration Preference Group",
    subtitle = ""
  ) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(size = 11)
  )




  
```






```


```
# Create the heatmap
p_heatmap <- correlation_data %>%
  ggplot(aes(x = immigrant_attitude, y = refugee_attitude, fill = percentage)) +
  geom_tile(color = "white", size = 0.5) +
  geom_text(aes(label = ifelse(percentage > 0, paste0(percentage, "%"), "")), 
            size = 3, color = "white", fontface = "bold") +
  facet_wrap(~ segment, ncol = 3) +
  scale_fill_gradient2(
    low = "white", 
    mid = "#fee08b",
    high = "#d73027", 
    midpoint = 15,
    name = "% of\nSegment",
    limits = c(0, NA)
  ) +
  labs(
    title = "Immigration vs Refugee Attitudes: Agreement Patterns by Segment",
    subtitle = "Diagonal shows where attitudes are identical (perfect agreement)",
    x = "Immigration Attitude",
    y = "Refugee Attitude"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(angle = 0, hjust = 1),
    legend.position = "right"
  )

print(p_heatmap)

```

```{r}

# Create data for "Reduce numbers" correlation heatmap
reduce_numbers_data <- segment_attitudes %>%
  mutate(
    immigrant_reduce = ifelse(immigrant_attitude == "Reduce numbers", 1, 0),
    refugee_reduce = ifelse(refugee_attitude == "Reduce numbers", 1, 0)
  ) %>%
  group_by(segment) %>%
  summarise(
    immigrant_reduce_pct = round(mean(immigrant_reduce, na.rm = TRUE) * 100, 0),
    refugee_reduce_pct = round(mean(refugee_reduce, na.rm = TRUE) * 100, 0),
    .groups = "drop"
  ) %>%
  # Calculate difference (can help identify patterns)
  mutate(
    difference = immigrant_reduce_pct - refugee_reduce_pct,
    avg_reduce = round((immigrant_reduce_pct + refugee_reduce_pct) / 2, 0)
  )

# Reshape for heatmap
heatmap_data <- reduce_numbers_data %>%
  select(segment, immigrant_reduce_pct, refugee_reduce_pct) %>%
  pivot_longer(
    cols = c(immigrant_reduce_pct, refugee_reduce_pct),
    names_to = "question_type",
    values_to = "percentage"
  ) %>%
  mutate(
    question_type = case_when(
      question_type == "immigrant_reduce_pct" ~ "Immigrants",
      question_type == "refugee_reduce_pct" ~ "Refugees"
    )
  )

# Create the correlation heatmap
p_reduce_heatmap <- heatmap_data %>%
  ggplot(aes(x = question_type, y = fct_reorder(segment, percentage), fill = percentage)) +
  geom_tile(color = "white", size = 1) +
  geom_text(aes(label = paste0(percentage, "%")), 
            size = 4, color = "white", fontface = "bold") +
  scale_fill_gradient2(
    low = "#fee08b", 
    mid = "#fd8d3c",
    high = "#d73027", 
    midpoint = 50,
    name = "% Wanting\nto Reduce",
    limits = c(0, 100)
  ) +
  labs(
    title = 'Correlation Heatmap: "Reduce Numbers" Attitudes',
    subtitle = "Percentage wanting to reduce numbers by segment and question type",
    x = "",
    y = "Segment"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 10),
    legend.position = "right",
    plot.title = element_text(size = 14, face = "bold")
  )

print(p_reduce_heatmap)


```

```{r}


anti_immigration_sentiment <- data %>%
  select(gender, age_grouped, region, ethnicity, education, degree, urbanrural, 
         religion, workstatus, finances, ownrent, leaveremain, 
         votingintention_headline, immigrant_numbers) %>%
  filter(!is.na(immigrant_numbers))

# Function to analyze anti-immigration sentiment by demographic
analyze_anti_immigration <- function(data, demographic_var) {
  data %>%
    group_by(!!sym(demographic_var)) %>%
    summarise(
      total_responses = n(),
      anti_immigration_count = sum(immigrant_numbers %in% c(
        "Government should significantly reduce the numbers",
        "Government should slightly reduce the numbers"
      ), na.rm = TRUE),
      anti_immigration_share = anti_immigration_count / total_responses * 100,
      .groups = 'drop'
    ) %>%
    filter(total_responses >= 50) %>%
    arrange(desc(anti_immigration_share)) %>%
    mutate(demographic_category = demographic_var) %>%
    select(demographic_category, category = !!sym(demographic_var), 
           total_responses, anti_immigration_count, anti_immigration_share)
}

# List of demographic variables to analyze
demographic_vars <- c("gender", "age_grouped", "region", "ethnicity", "education", 
                     "degree", "urbanrural", "religion", "workstatus", "finances", 
                     "ownrent", "leaveremain", "votingintention_headline")

# Analyze each demographic variable
results_list <- map(demographic_vars, ~analyze_anti_immigration(anti_immigration_sentiment, .x))
all_results <- bind_rows(results_list)

# Clean data: fix Reform UK, trim whitespace, and remove NAs in key variables
anti_immigration_sentiment_clean <- anti_immigration_sentiment %>%
  mutate(
    votingintention_headline = case_when(
      str_detect(votingintention_headline, "Reform") ~ "Reform UK",
      TRUE ~ votingintention_headline
    ),
    # Simplify religion labels
    religion = case_when(
      str_detect(religion, "Christian") ~ "Christian",
      TRUE ~ religion
    ),
    across(where(is.character), str_trim)
  ) %>%
  filter(
    !is.na(immigrant_numbers),
    !is.na(gender),
    !is.na(votingintention_headline),
    !is.na(ownrent)
  )

# Re-analyze with cleaned data
results_list_clean <- map(demographic_vars, ~analyze_anti_immigration(anti_immigration_sentiment_clean, .x))
all_results_clean <- bind_rows(results_list_clean)

# Get top group per demographic
top_per_demographic <- all_results_clean %>%
  group_by(demographic_category) %>%
  slice_max(anti_immigration_share, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  arrange(desc(anti_immigration_share))

# Prepare label without sample size
top_per_demographic <- top_per_demographic %>%
  mutate(label = paste0(demographic_category, ": ", category))

ggplot(top_per_demographic, 
       aes(x = anti_immigration_share,
           y = reorder(label, anti_immigration_share))) +
  geom_point(color = "blue", size = 3) +
  labs(
    title = "Groups with Highest Anti-Immigration Sentiment",
    subtitle = "",
    x = "Anti-Immigration Share (%)",
    y = "",
    caption = "Anti-immigration = 'Government should significantly/slightly reduce numbers'\nCategories with <50 respondents excluded"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold")
  ) +
  scale_x_continuous(limits = c(60, 90), breaks = seq(60, 90, 5))

```

```{r}
anti_refugees_sentiment <- data %>%
  select(gender, age_grouped, region, ethnicity, education, degree, urbanrural, 
         religion, workstatus, finances, ownrent, leaveremain, 
         votingintention_headline, refugees_numbers) %>%
  filter(!is.na(refugees_numbers))

# Function to analyze anti-immigration sentiment by demographic
analyze_anti_refugees <- function(data, demographic_var) {
  data %>%
    group_by(!!sym(demographic_var)) %>%
    summarise(
      total_responses = n(),
      anti_refugees_count = sum(refugees_numbers %in% c(
        "Government should significantly reduce the numbers",
        "Government should slightly reduce the numbers"
      ), na.rm = TRUE),
      anti_refugees_share = anti_refugees_count / total_responses * 100,
      .groups = 'drop'
    ) %>%
    filter(total_responses >= 50) %>%
    arrange(desc(anti_refugees_share)) %>%
    mutate(demographic_category = demographic_var) %>%
    select(demographic_category, category = !!sym(demographic_var), 
           total_responses, anti_refugees_count, anti_refugees_share)
}

# List of demographic variables to analyze
demographic_vars <- c("gender", "age_grouped", "region", "ethnicity", "education", 
                     "degree", "urbanrural", "religion", "workstatus", "finances", 
                     "ownrent", "leaveremain", "votingintention_headline")

# Analyze each demographic variable
results_list <- map(demographic_vars, ~analyze_anti_refugees(anti_refugees_sentiment, .x))
all_results <- bind_rows(results_list)

# Clean data: fix Reform UK, trim whitespace, and remove NAs in key variables
anti_refugees_sentiment_clean <- anti_refugees_sentiment %>%
  mutate(
    votingintention_headline = case_when(
      str_detect(votingintention_headline, "Reform") ~ "Reform UK",
      TRUE ~ votingintention_headline
    ),
    # Simplify religion labels
    religion = case_when(
      str_detect(religion, "Christian") ~ "Christian",
      TRUE ~ religion
    ),
    across(where(is.character), str_trim)
  ) %>%
  filter(
    !is.na(refugees_numbers),
    !is.na(gender),
    !is.na(votingintention_headline),
    !is.na(ownrent)
  )

# Re-analyze with cleaned data
results_list_clean <- map(demographic_vars, ~analyze_anti_refugees(anti_refugees_sentiment_clean, .x))
all_results_clean <- bind_rows(results_list_clean)

# Get top group per demographic
top_per_demographic <- all_results_clean %>%
  group_by(demographic_category) %>%
  slice_max(anti_refugees_share, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  arrange(desc(anti_refugees_share))

# Prepare label without sample size
top_per_demographic <- top_per_demographic %>%
  mutate(label = paste0(demographic_category, ": ", category))

# Plot with all requested changes
ggplot(top_per_demographic, 
       aes(x = anti_refugees_share,
           y = reorder(label, anti_refugees_share))) +
  geom_point(color = "blue", size = 3) +
  labs(
    title = "Groups with Highest Anti-Refugees Sentiment",
    subtitle = "",
    x = "Anti-Refugees Share (%)",
    y = "",
    caption = "Anti-immigration = 'Government should significantly/slightly reduce numbers'\nCategories with <50 respondents excluded"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold")
  ) +
  scale_x_continuous(limits = c(60, 90), breaks = seq(60, 90, 5))

```

```{r}

library(dplyr)
library(ggplot2)
library(scales)



library(dplyr)
library(ggplot2)
library(scales)

# Collapse immigrant_numbers into three categories
df <- data %>%
  mutate(
    migration_pref = case_when(
      immigrant_numbers %in% c(
        "Government should significantly increase the numbers",
        "Government should slightly increase the numbers"
      ) ~ "Increase",
      immigrant_numbers == "Government should keep the number the same" ~ "Keep the same",
      immigrant_numbers %in% c(
        "Government should slightly reduce the numbers",
        "Government should significantly reduce the numbers"
      ) ~ "Reduce",
      TRUE ~ NA_character_
    ),
    migration_pref = factor(migration_pref, levels = c("Increase", "Keep the same", "Reduce"))
  )

# Calculate percentages WITHIN each migration preference group
plot_data <- df %>%
  filter(!is.na(migration_pref), !is.na(political_interest)) %>%
  group_by(migration_pref, political_interest) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(migration_pref) %>%
  mutate(
    pct = n / sum(n)  # Percentage within each migration group
  ) %>%
  ungroup()

# Plot: Stacked bars (100% within each migration group)
ggplot(plot_data, aes(x = migration_pref, y = pct, fill = political_interest)) +
  geom_col(position = "fill") +
  geom_text(
    aes(label = ifelse(pct >= 0.05, percent(pct, accuracy = 1), "")),
    position = position_fill(vjust = 0.5),
    color = "white",
    size = 3.5
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    x = "Migration Preference",
    y = "Percentage of Respondents",
    fill = "Political Interest",
    title = "Political Interest Distribution Within Each Migration Preference Group",
    subtitle = ""
  ) +
  theme_minimal()
