

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rio)
library(survey)
library(svrepmisc)
library(marginaleffects)
library(patchwork)
```

## Data Prep


```{r echo=FALSE}
library(tidyverse)
library(rio)

dat <- import("immigration.csv")
dat <- dat %>% 
  mutate(gender = factor(gender, levels=c("Male", "Female")), 
         age_grouped = factor(age_grouped), 
         region = factor(region, 
                         levels = c("South West England", 
                                    "South East England", 
                                    "Greater London", 
                                    "East of England", 
                                    "West Midlands", 
                                    "Wales", 
                                    "East Midlands", 
                                    "Yorkshire and the Humber", 
                                    "North West England", 
                                    "North East England", 
                                    "Scotland")), 
         ethnicity = factor(ethnicity, levels=c("White (British/Irish/Other)", 
                                                "Asian/Asian British", 
                                                "Black/Black British",  
                                                "Mixed descent (e.g. White & Asian, White & Black)", 
                                                "Other"), 
                            labels = c("White", "Asian", "Black", "Mixed", "Other")),
         education = factor(education, 
                            levels = c("Incomplete Secondary Education (Below GCSE/O Level)",             
                                       "Secondary Education Completed (GCSE/O Level/CSE or equivalent)",
                                       "Secondary Education Completed (A Level or equivalent)",
                                       "Some Vocational or Technical Qualifications",
                                       "Vocational or Technical Qualifications Completed (e.g. HND, NVQ)",
                                       "University Education Completed (First Degree e.g. BA, BSc)",         
                                       "Postgraduate Education Completed (e.g. Masters)",   
                                       "Doctorate, Post-doctorate or equivalent (Higher Degree)",                                
                                       "Prefer not to answer"), 
                            labels = c("< Secondary", "Secondary < A Level", "Secondary A Level", 
                                       "Some Tech", "Tech Completed", "BA/Sc", "MA/Sc", "PhD", "No Answer")), 
         degree = factor(degree, 
                         levels = c("No degree", "Degree", ""), 
                         labels = c("No Degree", "Degree", "No Answer")), 
         urbanrural = factor(urbanrural, levels=c("Rural Area", "Village", "Small Town", "Large Town", "Suburbs", "Urban/City Centre"), 
                             labels = c("Rural", "Village", "Small Town", "Large Town", "Suburbs", "City")), 
         religion = factor(religion, levels=c("Christian (including Church of England, Catholic, Protestant and all other Christian denominations)", 
                                              "Muslim", "Hindu", "Jewish", "Buddhist", "Sikh", "Any other religion, write in", 
                                              "No religion", "Prefer not to say"), 
                           labels = c("Christian", "Muslim", "Hindu", "Jewish", "Buddhist", "Sikh", "Other", "None", "No Answer")), 
         christian = case_when(
           religion == "Christian" ~ "Christian", 
           religion %in% c("Muslim", "Hindu", "Jewish", "Buddhist", "Sikh", "Other") ~ "Other", 
           religion == "None" ~ "None", 
           religion == "No Answer" ~ "No Answer"
         ), 
         christian = factor(christian, levels=c("None", "Christian", "Other", "No Answer")), 
         workstatus = factor(workstatus, 
                             levels = c("Not working and not seeking work",
                                        "Homemaker/Househusband/Housewife etc",
                                        "Student",
                                        "Not working/temporarily unemployed/sick but seeking work",
                                        "Working part time - working less than 30 hours per week",
                                        "Working full time - working 30 hours per week or more",                              
                                        "Retired with a private pension",
                                        "Retired on a state pension only",                                              
                                        "Prefer not to say"), 
                             labels = c("Not Working", "Homemaker", "Student", "Unemployed", 
                                        "Part time", "Full time", "Retired Private Pension", 
                                        "Retired State Pension", "No Answer")), 
         work_small = case_when(
           workstatus %in% c("Not Working", "Homemaker", "Student") ~ "Not Working",
           workstatus == "Unemployed" ~ "Unemployed", 
           workstatus %in% c("Part time", "Full time") ~ "Working", 
           workstatus %in% c("Retired Private Pension", "Retired State Pension") ~ "Retired", 
           workstatus == "No Answer" ~ "No Answer"
         ),
         work_small = factor(work_small, levels=c("Not Working", "Unemployed", "Working", "Retired", "No Answer")), 
         finances = factor(finances, 
                           levels=c("I cannot afford my costs and often have to go without essentials like food and heating",
                                    "I can only just afford my costs and often struggle to make ends meet",
                                    "I do not have money for luxuries but can normally comfortably cover the essentials",
                                    "I am relatively comfortable financially",
                                    "I am very comfortable financially"), 
                           labels=c("Struggling", "Barely Managing", "Managing", "Comfortable", "Very Comfortable")), 
         ownrent = factor(ownrent, 
                          levels = c("Rent free", 
                                     "Rented from the council",
                                     "Rented from the housing association", 
                                     "Privately rented",
                                     "Owned with a mortgage or loan",
                                     "Owned outright",                                         
                                     "Prefer not to say"), 
                          labels = c("Rent Free", "Council Rent", "Housing Association Rent",
                                     "Private Rent", "Owned Mortgage", "Owned Outright", "No Answer")),
         ownrent_small = case_when(
           ownrent == "Rent Free" ~ "Rent Free", 
           ownrent %in% c("Council Rent", "Housing Association Rent", "Private Rent") ~ "Rent",
           ownrent %in% c("Owned Mortgage", "Owned Outright") ~ "Own",
           ownrent == "No Answer" ~ "No Answer"),
         ownrent_small = factor(ownrent_small, levels=c("Rent", "Rent Free", "Own", "No Answer")), 
         leaveremain = factor(leaveremain, 
                              levels=c("Remain", "Leave", "I did not vote", "I was too young to vote", "Don't know"), 
                              labels=c("Remain", "Leave", "No vote", "Too young", "DK")),
         leaveremain_small = case_when(
           leaveremain == "Remain" ~ "Remain", 
           leaveremain == "Leave" ~ "Leave", 
           leaveremain %in% c("No vote", "Too young", "DK") ~ "No Vote/DK"),
         leaveremain_small = factor(leaveremain_small, levels=c("Remain", "Leave", "No Vote/DK")), 
         scot_ref = factor(indyref, 
                           levels=c("AGAINST Scottish Independence", "FOR Scottish independence", 
                                    "I did not vote", "", "Don't Know"), 
                           labels = c("Against", "For", "Abstain", "Ineligible", "DK")), 
         vote2019 = case_when(
           grepl("Conserv", ge2019) ~ "Con", 
           grepl("Labour", ge2019) ~ "Lab",
           grepl("Liberal", ge2019) ~ "Lib Dem",
           grepl("SNP", ge2019) ~ "SNP",
           grepl("Green", ge2019) ~ "Green", 
           grepl("Brexit", ge2019) ~ "Brexit",
           grepl("Plaid Cymru", ge2019) ~ "Plaid Cymru",
           ge2019 == "Another party" ~ "Other", 
           ge2019 %in% "I did not/could not vote" ~ "Abstain", 
           ge2019 %in% c("Can't remember", "Don't know") ~ "DK"), 
         vote2019 = factor(vote2019, levels=c("Lab", "SNP", "Green", "Lib Dem", "Plaid Cymru", "Con", "Brexit")), 
         vote2024 = case_when(
           grepl("Conserv", ge2024) ~ "Con", 
           grepl("Labour", ge2024) ~ "Lab",
           grepl("Liberal", ge2024) ~ "Lib Dem",
           grepl("SNP", ge2024) ~ "SNP",
           grepl("Green", ge2024) ~ "Green", 
           grepl("Reform", ge2024) ~ "Reform",
           grepl("Plaid Cymru", ge2024) ~ "Plaid Cymru",
           grepl("Another", ge2024) ~ "Other", 
           ge2024 %in% "I did not/could not vote" ~ "Abstain", 
           ge2024 %in% c("Can't remember", "Don't know") ~ "DK"), 
         vote2024 = factor(vote2024, levels=c("Lab", "SNP", "Green", "Lib Dem", "Plaid Cymru", "Con", "Reform")), 
         likevote = as.numeric(likelihoodtovote), 
         likevote = case_when(
           likelihoodtovote == "0 - Certain not to vote" ~ 0, 
           likelihoodtovote == "10 - Certain to vote" ~ 10,
           likelihoodtovote == "Don't know" ~ NA_integer_,
           TRUE ~ likevote), 
         votingintention_headline = factor(votingintention_headline, 
                                           levels=c("Labour", "Scottish National Party (SNP)", "The Green Party", "Liberal Democrat", "Plaid Cymru", 
                                                    "Conservative", "Reform UK", "Another party/Independent Candidate", ""), 
                                           labels = c("Lab", "SNP", "Green", "Lib Dem", "Plaid Cymru", "Con", "Reform", "Other", "None")), 
         across(starts_with("biggest"), ~case_when(.x == "Not Selected" ~ 0, .x == "Selected" ~ 1, TRUE ~ NA_integer_)),
         political_attention = factor(political_attention, 
                                      levels=c("None at all", "A little", "A moderate amount", "A lot", "A great deal")), 
         political_interest = factor(political_interest, 
                                     levels=c("Not interested at all", "Hardly interested", "Quite interested", "Very interested"), 
                                     labels=c("None", "Little", "Quite", "Very")), 
         across(c(immigrant_numbers, refugees_numbers), 
                ~factor(.x, 
                        levels=c("Government should significantly reduce the numbers", 
                                 "Government should slightly reduce the numbers", 
                                 "Government should keep the number the same", 
                                 "Government should slightly increase the numbers", 
                                 "Government should significantly increase the numbers", 
                                 "Don’t know"), 
                        labels=c("Significantly Reduce", "Slightly Reduce", "Keep Same", "Slightly Increase", "Significantly Increase", "DK"))), 
         crossingsconcern = factor(crossingsconcern, 
                                   levels=c("Not at all concerned", "Not very concerned", "Somewhat concerned", "Very concerned"), 
                                   labels=c("None", "Not very", "Somewhat", "Very")), 
         labour_policy = factor(labour_policy, 
                                levels = c("The Labour Government wants to reduce the overall numbers coming to the UK", 
                                           "The Labour Government wants to keep the overall numbers the same", 
                                           "The Labour Government wants to increase the overall numbers coming to the UK", 
                                           "Don't know"), 
                                labels = c("Reduce", "Keep Same", "Increase", "DK")), 
         segment = factor(segment, 
                          levels=c("Progressive Activists", "Civic Pragmatists", "Disengaged Battlers",
                                   "Established Liberals",  "Loyal Nationals", "Disengaged Traditionalists",  "Backbone Conservatives"))
  ) %>% 
  rename("issue_afford_housing" = "biggestissue:Affordable housing",                 
         "issue_asylum_seeker" = "biggestissue:Asylum seekers crossing the channel",
         "issue_brexit" = "biggestissue:Brexit",                             
         "issue_climate" = "biggestissue:Climate change and the environment", 
         "issue_immigration" = "biggestissue:Levels of immigration",              
         "issue_costs" = "biggestissue:Cost of living",                     
         "issue_education" = "biggestissue:Education and childcare",            
         "issue_crime" = "biggestissue:Crime",                              
         "issue_care_elderly" = "biggestissue:Social care for the elderly",        
         "issue_jobs" = "biggestissue:Jobs and unemployment",              
         "issue_mental_health" = "biggestissue:Mental health",                      
         "issue_middle_east" = "biggestissue:Conflict in the Middle East",        
         "issue_trans" = "biggestissue:The debate about transgender people",
         "issue_nhs" = "biggestissue:Supporting the NHS",                 
         "issue_ukraine" = "biggestissue:The war in Ukraine",                 
         "issue_welfare" = "biggestissue:Welfare and benefits",               
         "issue_other" = "biggestissue:Other (please specify)",
         "issue_none" = "biggestissue:None of the above")                        


dat <- dat %>% 
  mutate(immig_num2 = case_when(
    grepl("Reduce", immigrant_numbers) ~ "Reduce",
    grepl("Increase", immigrant_numbers) ~ "Increase", 
    TRUE ~ "Keep Same/DK"), 
    immig_num2 = factor(immig_num2, 
                        levels = c("Reduce", "Keep Same/DK", "Increase")), 
    refugee_num2 = case_when(
      grepl("Reduce", refugees_numbers) ~ "Reduce",
      grepl("Increase", refugees_numbers) ~ "Increase", 
      TRUE ~ "Keep Same/DK"), 
    refugee_num2 = factor(refugee_num2, 
                          levels = c("Reduce", "Keep Same/DK", "Increase")))

dat2 <- dat %>% 
  mutate(
    education = case_when(education == "No Answer" ~ NA_character_, TRUE ~ education), 
    education = factor(education, levels = levels(dat$education[1:8])), 
    educ3 = case_when(
      grepl("Secondary", education) ~ "Secondary or Less", 
      grepl("Tech", education) ~ "Tech Training", 
      education %in% c("BA/Sc", "MA/Sc", "PhD") ~ "Degree",
      TRUE ~ NA_character_), 
    educ3 = factor(educ3, 
                   levels = c("Secondary or Less", "Tech Training", "Degree"), 
                   labels = c("Secondary or Less", "Tech Training", "Degree")), 
    urbrur3 = case_when(
      urbanrural %in% c("Rural", "Village") ~ "Rural", 
      urbanrural %in% c("Small Town", "Large Town", "Suburbs") ~ "Town/Suburb", 
      urbanrural == "City" ~ "City"), 
    finances3 = case_when(
      finances %in% c("Barely Managing", "Struggling") ~ "Struggling",
      finances == "Managing" ~ "Managing",
      finances %in% c("Comfortable", "Very Comfortable") ~ "Comfortable",
    ), 
    ownrent2 = case_when(
      grepl("Rent", ownrent) ~ "Rent",
      grepl("Own", ownrent) ~ "Own",
      TRUE ~ "No Answer"
    ), 
    youngold = case_when(
      age_grouped %in% c("18-24", "25-34", "35-44") ~ "Young",
      age_grouped %in% c("45-54", "55-64", "65+") ~ "Older"
    ), 
    vote_right = case_when(
      votingintention_headline %in% c("Con", "Reform") ~ "Right",
      votingintention_headline %in% c("Lab", "SNP", "Green", "Lib Dem", "Plaid Cymru", "Ohter") ~ "Left", 
      votingintention_headline == "None" ~ "No Vote"
    ), 
    degree = case_when(
      degree == "No Answer" ~ NA_character_,
      TRUE ~ degree
    ), 
    degree = factor(degree, levels=c("No Degree", "Degree"))
  )
```


## Model 1

```{r fig.height=10, fig.width=6, out.width="100%"}
m0 <- nnet::multinom(segment ~ immig_num2 + youngold + gender + degree + urbrur3 + finances3 + ethnicity + ownrent2 +  vote_right + 
                       region + work_small + political_interest + crossingsconcern + 
                       leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate +  
                       issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                     data=subset(dat2, issue_immigration == 0), maxit=1000, trace=FALSE)

m1 <- nnet::multinom(segment ~ immig_num2 + youngold + gender + degree + urbrur3 + finances3 + ethnicity + ownrent2 +   vote_right + 
                       region + work_small + political_interest + crossingsconcern + 
                       leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                       issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                     data=subset(dat2, issue_immigration == 1), maxit=1000, trace=FALSE)


library(marginaleffects)

p1 <- avg_predictions(m1, variables = "immig_num2")
p0 <- avg_predictions(m0, variables = "immig_num2")

plot_dat <- bind_rows(p0 %>% as.data.frame() %>% mutate(iss = "Immigration Not Important"),
                      p1 %>% as.data.frame() %>% mutate(iss = "Immigration Important"))

ggplot(plot_dat, aes(x=group, y=estimate, ymin=conf.low, ymax=conf.high, colour=iss)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~forcats::fct_rev(immig_num2), ncol=1) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Segment Membership", colour="") + 
  scale_color_brewer(palette = "Set1")
```

```{r}
ggplot(plot_dat, aes(x=immig_num2, y=estimate, ymin=conf.low, ymax=conf.high, colour=iss)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~group) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Segment Membership", colour="") + 
  scale_color_brewer(palette = "Set1")


```


```{r}
ggplot(plot_dat, aes(x=as.numeric(immig_num2), y=estimate, ymin=conf.low, ymax=conf.high, colour=iss)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  geom_line() + 
  facet_grid(group~iss) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Segment Membership", colour="") + 
  scale_color_brewer(palette = "Set1") + 
  scale_x_continuous(breaks=1:3, labels=c("Reduce", "Keep Same", "Increase")) 

```

```{r}
ggplot(plot_dat, aes(x=as.numeric(immig_num2), y=estimate, ymin=conf.low, ymax=conf.high, colour=iss)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  geom_line() + 
  facet_grid(group~iss) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Segment Membership", colour="") + 
  scale_color_brewer(palette = "Set1") + 
  scale_x_continuous(breaks=1:3, labels=c("Reduce", "Keep Same", "Increase")) 

```



If want to know which comparisons are significant, look here: 

```{r}
c1a <- avg_comparisons(m0, variables=list("immig_num2" = "pairwise"))
c1b <- avg_comparisons(m1, variables=list("immig_num2" = "pairwise"))
comp_dat1 <- bind_rows(c1a %>% as.data.frame() %>% mutate(immig_imp = "Immigration Not Important"),
                       c1b %>% as.data.frame() %>% mutate(immig_imp = "Immigration Important")) %>% 
  mutate(immig_imp = factor(immig_imp, levels=c("Immigration Not Important", "Immigration Important"))) %>% 
  mutate(sig = ifelse(p.value < .05, "Significant", "Not Significant")) 
comp_dat1 %>% select(group, contrast, estimate, sig)
```

## Model 2

```{r fig.height=4, fig.width=10, out.width="100%"}
m2a <- MASS::polr(immig_num2 ~ youngold + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + 
                       region + work_small + political_interest + crossingsconcern + 
                       leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                       issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                     data=subset(dat2, urbrur3 == "Rural"))

m2b <- MASS::polr(immig_num2 ~ youngold + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, urbrur3 == "Town/Suburb"))

m2c <- MASS::polr(immig_num2 ~ youngold + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, urbrur3 == "City"))

p2a <- avg_predictions(m2a, variables = "degree")
p2b <- avg_predictions(m2b, variables = "degree")
p2c <- avg_predictions(m2c, variables = "degree")
plot_dat2 <- bind_rows(p2a %>% as.data.frame() %>% mutate(urbrur = "Rural"),
                       p2b %>% as.data.frame() %>% mutate(urbrur = "Town/Suburb"),
                       p2c %>% as.data.frame() %>% mutate(urbrur = "City")) %>% 
  mutate(urbrur = factor(urbrur, levels=c("Rural", "Town/Suburb", "City")))

ggplot(plot_dat2, aes(x=urbrur, y=estimate, ymin=conf.low, ymax=conf.high, colour=degree)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~forcats::fct_rev(group), nrow=1) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Holding Immigration Preference", colour="") + 
  scale_color_brewer(palette = "Set1") 
```

To see whcih comparisons are significant, look here:

```{r}
c2a <- avg_comparisons(m2a, variables="degree")
c2b <- avg_comparisons(m2b, variables="degree")
c2c <- avg_comparisons(m2c, variables="degree")
comp_dat2 <- bind_rows(c2a %>% as.data.frame() %>% mutate(urbrur = "Rural"),
                       c2b %>% as.data.frame() %>% mutate(urbrur = "Town/Suburb"),
                       c2c %>% as.data.frame() %>% mutate(urbrur = "City")) %>% 
  mutate(urbrur = factor(urbrur, levels=c("Rural", "Town/Suburb", "City"))) %>% 
  mutate(sig = ifelse(p.value < .05, "Significant", "Not Significant")) 
comp_dat2 %>% select(group, urbrur, contrast, estimate, sig)
```
## Model 3

```{r fig.height=4, fig.width=10, out.width="100%"}
m3a <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, youngold == "Young"))

m3b <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, youngold == "Older"))


p3a <- avg_predictions(m3a, variables = "gender")
p3b <- avg_predictions(m3b, variables = "gender")
plot_dat3 <- bind_rows(p3a %>% as.data.frame() %>% mutate(age = "Young"),
                       p3b %>% as.data.frame() %>% mutate(age = "Older")) %>% 
  mutate(age = factor(age, levels=c("Young", "Older")))

ggplot(plot_dat3, aes(x=age, y=estimate, ymin=conf.low, ymax=conf.high, colour=gender)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~forcats::fct_rev(group), nrow=1) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Holding Immigration Preference", colour="") + 
  scale_color_brewer(palette = "Set1") 

```

To see which comparisons are significant, look here: 

```{r}
c3a <- avg_comparisons(m3a, variables="gender")
c3b <- avg_comparisons(m3b, variables="gender")
comp_dat3 <- bind_rows(c3a %>% as.data.frame() %>% mutate(age = "Young"),
                       c3b %>% as.data.frame() %>% mutate(age = "Older")) %>% 
  mutate(age = factor(age, levels=c("Young", "Older"))) %>% 
  mutate(sig = ifelse(p.value < .05, "Significant", "Not Significant")) 
comp_dat3 %>% select(group, age, contrast, estimate, sig)
```

## Model 4

```{r fig.height=4, fig.width=10, out.width="100%"}
m4a <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, vote_right == "Right"))

m4b <- MASS::polr(immig_num2 ~ youngold + urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_afford_housing + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, vote_right == "Left"))


p4a <- avg_predictions(m4a, variables = "finances3")
p4b <- avg_predictions(m4b, variables = "finances3")
plot_dat4 <- bind_rows(p4a %>% as.data.frame() %>% mutate(vote = "Right"),
                       p4b %>% as.data.frame() %>% mutate(vote = "Left")) %>% 
  mutate(vote = factor(vote, levels=c("Left", "Right")), 
         finances3 = factor(finances3, 
                            levels=c("Struggling", "Managing", "Comfortable")))

ggplot(plot_dat4, aes(x=finances3, y=estimate, ymin=conf.low, ymax=conf.high, colour=vote)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~forcats::fct_rev(group), nrow=1) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Holding Immigration Preference", colour="") + 
  scale_color_brewer(palette = "Set1") 

```

To see which comparisons are significant, look here: 

```{r}
c4a <- avg_comparisons(m4a, variables=list("finances3" = "pairwise"))
c4b <- avg_comparisons(m4b, variables=list("finances3" = "pairwise"))
comp_dat4 <- bind_rows(c4a %>% as.data.frame() %>% mutate(vote = "Right"),
                       c4b %>% as.data.frame() %>% mutate(vote = "Left")) %>% 
  mutate(age = factor(vote, levels=c("Left", "Right"))) %>% 
  mutate(sig = ifelse(p.value < .05, "Significant", "Not Significant")) 
comp_dat4 %>% select(group, vote, contrast, estimate, sig)
```

## Model 5

```{r fig.height=4, fig.width=10, out.width="100%"}
p5a <- avg_predictions(m3a, variables = "ownrent2")
p5b <- avg_predictions(m3b, variables = "ownrent2")
plot_dat5 <- bind_rows(p5a %>% as.data.frame() %>% mutate(age = "Young"),
                       p5b %>% as.data.frame() %>% mutate(age = "Older")) %>% 
  mutate(age = factor(age, levels=c("Young", "Older")))

ggplot(plot_dat5 %>% filter(ownrent2 != "No Answer"), aes(x=age, y=estimate, ymin=conf.low, ymax=conf.high, colour=ownrent2)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~forcats::fct_rev(group), nrow=1) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Holding Immigration Preference", colour="") + 
  scale_color_brewer(palette = "Set1") 
```

To see which comparisons are significant, look here: 

```{r}
c5a <- avg_comparisons(m3a, variables="ownrent2")
c5b <- avg_comparisons(m3b, variables="ownrent2")
comp_dat5 <- bind_rows(c5a %>% as.data.frame() %>% mutate(age = "Young"),
                       c5b %>% as.data.frame() %>% mutate(age = "Older")) %>% 
  mutate(age = factor(age, levels=c("Young", "Older"))) %>% 
  mutate(sig = ifelse(p.value < .05, "Significant", "Not Significant")) 
comp_dat5 %>% select(group, contrast, estimate, sig)
```


## Model 6

```{r fig.height=4, fig.width=10, out.width="100%"}
m6a <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + youngold + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small+ issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, issue_afford_housing == 0))

m6b <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + youngold + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, issue_afford_housing == 1))


p6a <- avg_predictions(m6a, variables = "youngold")
p6b <- avg_predictions(m6b, variables = "youngold")
plot_dat6 <- bind_rows(p6a %>% as.data.frame() %>% mutate(afford_house = "Not Selected"),
                       p6b %>% as.data.frame() %>% mutate(afford_house = "Selected")) %>% 
  mutate(afford_house = factor(afford_house, levels=c("Not Selected", "Selected")))

ggplot(plot_dat6, aes(x=afford_house, y=estimate, ymin=conf.low, ymax=conf.high, colour=youngold)) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~forcats::fct_rev(group), nrow=1) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Holding Immigration Preference", colour="") + 
  scale_color_brewer(palette = "Set1") 
```

To see which comparisons are significant, look here: 

```{r}
c6a <- avg_comparisons(m6a, variables="youngold")
c6b <- avg_comparisons(m6b, variables="youngold")
comp_dat6 <- bind_rows(c6a %>% as.data.frame() %>% mutate(afford_house = "Not Selected"),
                       c6b %>% as.data.frame() %>% mutate(afford_house = "Selected")) %>% 
  mutate(afford_house = factor(afford_house, levels=c("Not Selected", "Selected"))) %>% 
  mutate(sig = ifelse(p.value < .05, "Significant", "Not Significant")) 
comp_dat6 %>% select(afford_house, group, contrast, estimate, sig)

c6a <- avg_comparisons(m6a, variables="youngold") %>% inferences(method="simulation")
c6b <- avg_comparisons(m6b, variables="youngold") %>% inferences(method="simulation")

post6a <- t(attr(c6a, "posterior_draws"))
post6b <- t(attr(c6b, "posterior_draws"))

post6 <- cbind(post6a, post6b)
colnames(post6) <- c("R_NS", "K_NS", "I_NS", "R_S", "K_S", "I_S")
make_diff <- function(X, calc_secdiff = FALSE, ...){
  combs <- combn(ncol(X), 2)
  D <- matrix(0, nrow=ncol(X), ncol=ncol(combs))
  D[cbind(combs[1,], 1:ncol(combs))] <- -1
  D[cbind(combs[2,], 1:ncol(combs))] <- 1
  diffs <- X %*% D
  p_less <- apply(diffs, 2, \(x)mean(x < 0))
  p_eq <- apply(diffs, 2, \(x) mean(x == 0))
  p_more <- apply(diffs, 2, \(x)mean(x > 0))
  p_neq <- p_less + p_more  
  p <- dplyr::case_when(
    p_neq <= .9 ~ .5, 
    p_neq > .9 & p_more > p_less ~ p_more, 
    p_neq > .9 & p_less > p_more ~ p_less
  )
  out_fd <- tibble(
    col1 = colnames(X)[combs[1,]], 
    col2 = colnames(X)[combs[2,]], 
    diff = colMeans(diffs), 
    p = p)
  res <- list(fd = out_fd)
  if(calc_secdiff){
  cn <- paste(colnames(X)[combs[2,]], 
              colnames(X)[combs[1,]], 
              sep=" - ")
  X <- diffs
  colnames(X) <- cn
  combs <- combn(ncol(X), 2)
  D <- matrix(0, nrow=ncol(X), ncol=ncol(combs))
  D[cbind(combs[1,], 1:ncol(combs))] <- -1
  D[cbind(combs[2,], 1:ncol(combs))] <- 1
  diffs <- X %*% D
  p_less <- apply(diffs, 2, \(x)mean(x < 0))
  p_eq <- apply(diffs, 2, \(x) mean(x == 0))
  p_more <- apply(diffs, 2, \(x)mean(x > 0))
  p_neq <- p_less + p_more  
  p <- dplyr::case_when(
    p_neq <= .9 ~ .5, 
    p_neq > .9 & p_more > p_less ~ p_more, 
    p_neq > .9 & p_less > p_more ~ p_less
  )
  out_sd <- tibble(
    col1 = colnames(X)[combs[1,]], 
    col2 = colnames(X)[combs[2,]], 
    diff = colMeans(diffs),
    p = p)
    res$sd <- out_sd
  }
  return(res)
}

m6 <- make_diff(post6, calc_secdiff = TRUE)
```

```{r}
m7 <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + youngold + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small+ issue_brexit + issue_care_elderly + issue_climate + issue_afford_housing, 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=dat2)

mf <- model.frame(m7)[,1:14]
l <- lapply(names(mf), \(x)"pairwise")
names(l) <- colnames(mf)

pred7 <- avg_predictions(m7, variables = "crossingsconcern")

comp7 <- avg_comparisons(m7, variables = l)
comp7_best <- comp7 %>% 
  as.data.frame() %>% 
  group_by(term, group) %>% 
  slice_max(abs(estimate), n=1)

comp7_best %>% filter(group == "Reduce") %>% arrange(desc(abs(estimate)))

```




## Model 6

```{r fig.height=4, fig.width=10, out.width="100%"}
m8a <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + issue_afford_housing + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small+ issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, youngold == "Young"))

m8b <- MASS::polr(immig_num2 ~ urbrur3 + gender + degree + finances3 + ethnicity + ownrent2 +  vote_right + issue_afford_housing + 
                    region + work_small + political_interest + crossingsconcern + 
                    leaveremain_small + issue_brexit + issue_care_elderly + issue_climate + 
                    issue_costs + issue_crime + issue_jobs + issue_mental_health + issue_nhs + issue_ukraine + issue_welfare, 
                  data=subset(dat2, youngold == "Older"))


p8a <- avg_predictions(m8a, variables = "issue_afford_housing")
p8b <- avg_predictions(m8b, variables = "issue_afford_housing")
plot_dat8 <- bind_rows(p8a %>% as.data.frame() %>% mutate(youngold = "Young"),
                       p8b %>% as.data.frame() %>% mutate(youngold = "Older")) %>% 
  mutate(youngold = factor(youngold, levels=c("Young", "Older")))

ggplot(plot_dat8, aes(x=youngold, y=estimate, ymin=conf.low, ymax=conf.high, colour= as.factor(issue_afford_housing))) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  facet_wrap(~forcats::fct_rev(group), nrow=1) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Holding Immigration Preference", colour="") + 
  scale_color_brewer(palette = "Set1") 

ggplot(p8a, aes(x=group, y=estimate, ymin = conf.low, ymax=conf.high, 
                colour=factor(issue_afford_housing, levels=c(0,1), labels=c("Not Seleted", "Selected")))) + 
  geom_pointrange(position = position_dodge(width=.5)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1), 
        legend.position="top") +
  labs(x="", y="Probability of Holding Immigration Preference", colour="") + 
  scale_color_brewer(palette = "Set1") 
  

```

To see which comparisons are significant, look here: 

```{r}
c8a <- avg_comparisons(m8a, variables="issue_afford_housing")
c8b <- avg_comparisons(m8b, variables="issue_afford_housing")
comp_dat8 <- bind_rows(c8a %>% as.data.frame() %>% mutate(afford_house = "Not Selected"),
                       c8b %>% as.data.frame() %>% mutate(afford_house = "Selected")) %>% 
  mutate(afford_house = factor(afford_house, levels=c("Not Selected", "Selected"))) %>% 
  mutate(sig = ifelse(p.value < .05, "Significant", "Not Significant")) 
comp_dat8 %>% select(afford_house, group, contrast, estimate, sig)
```
